---
title: "Descriptive statistics"
author: "IBRAHIM KASSOUM Habibou"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
#  officedown::rdocx_document:
#    mapstyles:
#      Normal: ['First Paragraph']

knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, error=FALSE)
rm(list=ls())
```



## Importing library

```{r Package needed, results = "hide", include = FALSE, warning=FALSE, echo = TRUE}


## Importing library
### List of required packages
required_packages <- c("tidyverse","janitor" ,"readr","dplyr", "tidyverse","readxl",
                       "flextable","gtsummary","ggthemes", "lfe","stargazer","devtools")

# Check if packages are installed
missing_packages <- setdiff(required_packages, installed.packages()[,"Package"])

### Install missing packages
if (length(missing_packages) > 0) {
  install.packages(missing_packages)
}

### Load all packages
lapply(required_packages, library, character.only = TRUE)


# if not already installed
#install.packages('devtools', repos = 'http://cran.us.r-project.org') 

# note: "V" is capitalized
devtools::install_github('xuyiqing/panelView') 
devtools::install_github("hemken/Statamarkdown")
```


```{r, results='hide', include = FALSE, warning=FALSE, echo = FALSE}
# Read excel files data for the r1, r2 and r3

## For r1
df_r1_hh <- readxl::read_excel("output/data/r1_hh.xlsx")
df_r1_anthr1 <- readxl::read_excel("output/data/r1_overfive.xlsx")
df_r1_anthr2 <- readxl::read_excel("output/data/r1_underfive.xlsx")

## For r2
df_r2_hh <- readxl::read_excel("output/data/r2_hh.xlsx")
df_r2_anthr1 <- readxl::read_excel("output/data/r2_overfive.xlsx")
df_r2_anthr2 <- readxl::read_excel("output/data/r2_underfive.xlsx")

## For r3
df_r3_hh <- readxl::read_excel("output/data/r3_hh.xlsx")
df_r3_anthr1 <- readxl::read_excel("output/data/r3_overfive.xlsx")
df_r3_anthr2 <- readxl::read_excel("output/data/r3_underfive.xlsx")

```

```{r, results='hide', include = FALSE, warning=FALSE, echo = FALSE}


## Final dataset
# df_global_corrected <- readxl::read_excel("output/data/df_global_corrected.xlsx", 
#     col_types = c("skip", "text", "text", 
#         "numeric", "numeric", "text", "text", 
#         "text", "text", "numeric", "text", 
#         "text", "text", "text", "text", "text", 
#         "text", "text", "text", "numeric", 
#         "numeric", "numeric", "numeric"))
# 

df_global <- read_excel("output/data/df_global.xlsx")

df_global_corrected <- read_excel("output/data/df_global_corrected.xlsx")
```

```{r, results='hide', include = FALSE, warning=FALSE, echo = FALSE}
## define custom test
fisher.test.simulate.p.values <- function(data, variable, by, ...) {
  result <- list()
  test_results <- stats::fisher.test(data[[variable]], data[[by]], simulate.p.value = TRUE)
  result$p <- test_results$p.value
  result$test <- test_results$method
  result
}
```


## Analysis of missing values and migration or attrition by region and migration.


### Splitted hh
The split households are on average:

* Bigger in terms of size.
* Less likely to be female-headed.
* Have older heads.
* Have less educated heads.
* Have more female members.
* Have more children under five.
* Have more teenagers.
* Have more adults.
* Have more female adults and teenagers.
* Have more teenage adults.

```{r, results='hold', include = TRUE, warning=FALSE, echo = FALSE}
df_r1_hh %>% 
  mutate(hh_split_r2_r3 = ifelse(hh_split_r3=="1"| hh_split_r2=="1","1","0")) %>% 
  # Selecting relevant variables
   select(hh_id, hh_split_r2_r3,hh_size,affected_upazila,hh_head_religion,hh_ethnic_group) %>% 
  left_join(
    df_r1_anthr1 %>% 
      filter(relation_hhh=="primary respondent") %>% 
      select(high_exposed, exposed_at_least_zero, mean_speed, mean_time, hh_id, hhm_sex, hhm_age, marital_status_hhm, literacy_hhm, education_high, hhm_status, nbr_female, nbr_underfive, nbr_yngchldrn_5_10, nbr_teenager_10_20, nbr_adults_20_65, nbr_female_underfive, nbr_female_yngchldrn_5_10, nbr_female_teenager_10_20, nbr_female_adults_20_65)) %>% 
mutate(
  hh_split_r2_r3 = factor(hh_split_r2_r3, levels = c("0", "1"), labels = c("Don't split", "Split"), ordered = TRUE),
  affected_upazila = factor(affected_upazila, levels = c("0", "1")),
  high_exposed = factor(high_exposed, levels = c("0", "1")),
  exposed_at_least_zero = factor(exposed_at_least_zero, levels = c("0", "1")),
  mean_speed = as.numeric(mean_speed),
  mean_time = as.numeric(mean_time),
         nbr_female = as.numeric(nbr_female),
         nbr_underfive = as.numeric(nbr_underfive),
         nbr_yngchldrn_5_10 = as.numeric(nbr_yngchldrn_5_10),
         nbr_teenager_10_20 = as.numeric(nbr_teenager_10_20),
         nbr_adults_20_65 = as.numeric(nbr_adults_20_65),
         nbr_female_underfive = as.numeric(nbr_female_underfive),
         nbr_female_yngchldrn_5_10 = as.numeric(nbr_female_yngchldrn_5_10),
         nbr_female_teenager_10_20 = as.numeric(nbr_female_teenager_10_20),
         nbr_female_adults_20_65 = as.numeric(nbr_female_adults_20_65)) %>%
  select(-c(hh_id)) %>% 
      # Generate a summary table using "tbl_summary" for the specified columns
    tbl_summary(
    by = hh_split_r2_r3, 
     label = list(
       mean_speed ~ "Mean wind speed (in m/s)",
       mean_time ~ "Mean wind duration (in hours)",
       high_exposed ~ "Highly exposed union (Yes=1, No=0)",
       exposed_at_least_zero ~ "Exposed union (Yes=1, No=0)",
       hh_size ~ "Hh. size",
       hh_head_religion ~ "Hh. head rlgn",
       hh_ethnic_group  ~ "Hh. head ethnc",
       affected_upazila ~ "Affected upazila (Yes=1, No=0)",
       hhm_sex ~ "Hh. head sex", 
       hhm_age ~ "Hh. head age", 
       marital_status_hhm ~ "Hh. head mrtl stts", 
       literacy_hhm ~ "Hh. head ltrc" , 
       education_high ~ "Hh. head edctn", 
       hhm_status ~ "Hh. head stts",
       nbr_female ~ "Hh. nbr fml" , 
       nbr_underfive ~ "Hh. nbr undrfv" , 
       nbr_yngchldrn_5_10 ~ "Hh. nbr yng child (5-10)" , 
       nbr_teenager_10_20 ~ "Hh. nbr tngr (10-20)", 
       nbr_adults_20_65 ~ "Hh. nbr adlts (20-65)", 
       nbr_female_underfive ~ "Hh. nbr female undrfv", 
       nbr_female_yngchldrn_5_10 ~ "Hh. fml yng child (5-10)", 
       nbr_female_teenager_10_20 ~ "Hh. fml tngr (10-20)",
       nbr_female_adults_20_65 ~ "Hh. fml adlts (20-65)"),
    
    type = list(
      affected_upazila ~ "dichotomous",
      high_exposed ~ "dichotomous",
      exposed_at_least_zero ~ "dichotomous",
       nbr_female ~ "continuous" , 
       nbr_underfive ~ "continuous" , 
       nbr_yngchldrn_5_10 ~ "continuous" , 
       nbr_teenager_10_20 ~ "continuous", 
       nbr_adults_20_65 ~ "continuous", 
       nbr_female_underfive ~ "continuous", 
       nbr_female_yngchldrn_5_10 ~ "continuous", 
       nbr_female_teenager_10_20 ~ "continuous",
       nbr_female_adults_20_65 ~ "continuous"
      ),
    statistic = list(
      all_categorical() ~ "{n} ({p}%)",
      all_continuous() ~ "{mean} ({sd})"
    ),
    missing_text = "(Missing)",
    digits = list(all_continuous() ~ c(2,2)),
    missing = "ifany"
  ) %>%
       add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) %>% 
  modify_header(label ~ "") %>% 
  add_overall(last=TRUE)
```
```{r, results='hold', include = TRUE, warning=FALSE, echo = FALSE}

df_reg = df_r1_hh %>% 
                   mutate(hh_split_r2_r3 = ifelse(hh_split_r3=="1"|hh_split_r2=="1","1","0")) %>% 
  # Selecting relevant variables
   select(hh_id, hh_split_r2_r3,hh_size,affected_upazila,hh_head_religion,hh_ethnic_group) %>% 
  left_join(
    df_r1_anthr1 %>% 
      filter(relation_hhh=="primary respondent") %>% 
      select(hh_id, hhm_sex, hhm_age, marital_status_hhm, literacy_hhm, education_high, hhm_status, nbr_female, nbr_underfive, nbr_yngchldrn_5_10, nbr_teenager_10_20, nbr_adults_20_65, nbr_female_underfive, nbr_female_yngchldrn_5_10, nbr_female_teenager_10_20, nbr_female_adults_20_65,   high_exposed,exposed_at_least_zero)) %>% 
mutate(

  affected_upazila = factor(affected_upazila, levels = c("0", "1")),
  high_exposed = factor(high_exposed, levels = c("0", "1")),
  exposed_at_least_zero = factor(exposed_at_least_zero, levels = c("0", "1")),
         nbr_female = as.numeric(nbr_female),
         nbr_underfive = as.numeric(nbr_underfive),
         nbr_yngchldrn_5_10 = as.numeric(nbr_yngchldrn_5_10),
         nbr_teenager_10_20 = as.numeric(nbr_teenager_10_20),
         nbr_adults_20_65 = as.numeric(nbr_adults_20_65),
         nbr_female_underfive = as.numeric(nbr_female_underfive),
         nbr_female_yngchldrn_5_10 = as.numeric(nbr_female_yngchldrn_5_10),
         nbr_female_teenager_10_20 = as.numeric(nbr_female_teenager_10_20),
         nbr_female_adults_20_65 = as.numeric(nbr_female_adults_20_65)) %>%
  select(-c(hh_id))

reg0 <- felm(hh_split_r2_r3 ~ hhm_sex + hhm_age+ hh_size +  marital_status_hhm+ literacy_hhm+ education_high +  hh_head_religion + hh_ethnic_group + nbr_female+ nbr_underfive+ nbr_yngchldrn_5_10+ nbr_teenager_10_20+ nbr_adults_20_65+ nbr_female_underfive+ nbr_female_yngchldrn_5_10+ nbr_female_teenager_10_20+ nbr_female_adults_20_65, data=df_reg)

reg1 <- felm(hh_split_r2_r3 ~ affected_upazila + hhm_sex + hhm_age+ hh_size +  marital_status_hhm+ literacy_hhm+ education_high +  hh_head_religion + hh_ethnic_group + nbr_female+ nbr_underfive+ nbr_yngchldrn_5_10+ nbr_teenager_10_20+ nbr_adults_20_65+ nbr_female_underfive+ nbr_female_yngchldrn_5_10+ nbr_female_teenager_10_20+ nbr_female_adults_20_65, data=df_reg)

reg2 <- felm(hh_split_r2_r3 ~ exposed_at_least_zero + hhm_sex + hhm_age+ hh_size +  marital_status_hhm+ literacy_hhm+ education_high +  hh_head_religion + hh_ethnic_group + nbr_female+ nbr_underfive+ nbr_yngchldrn_5_10+ nbr_teenager_10_20+ nbr_adults_20_65+ nbr_female_underfive+ nbr_female_yngchldrn_5_10+ nbr_female_teenager_10_20+ nbr_female_adults_20_65, data=df_reg)

reg3 <- felm(hh_split_r2_r3 ~ high_exposed + hhm_sex + hhm_age+ hh_size +  marital_status_hhm+ literacy_hhm+ education_high +  hh_head_religion + hh_ethnic_group + nbr_female+ nbr_underfive+ nbr_yngchldrn_5_10+ nbr_teenager_10_20+ nbr_adults_20_65+ nbr_female_underfive+ nbr_female_yngchldrn_5_10+ nbr_female_teenager_10_20+ nbr_female_adults_20_65, data=df_reg)


reg4 <- felm(hh_split_r2_r3 ~ exposed_at_least_zero + hhm_sex + hhm_age+ hh_size +  marital_status_hhm+ literacy_hhm+ education_high +  hh_head_religion + hh_ethnic_group + nbr_female+ nbr_underfive+ nbr_yngchldrn_5_10+ nbr_teenager_10_20+ nbr_adults_20_65+ nbr_female_underfive+ nbr_female_yngchldrn_5_10+ nbr_female_teenager_10_20+ nbr_female_adults_20_65, data=df_reg)

reg5 <- felm(hh_split_r2_r3 ~ high_exposed + hhm_sex + hhm_age+ hh_size +  marital_status_hhm+ literacy_hhm+ education_high +  hh_head_religion + hh_ethnic_group + nbr_female+ nbr_underfive+ nbr_yngchldrn_5_10+ nbr_teenager_10_20+ nbr_adults_20_65+ nbr_female_underfive+ nbr_female_yngchldrn_5_10+ nbr_female_teenager_10_20+ nbr_female_adults_20_65, data=df_reg)



stargazer(reg0, reg1, reg2, reg3, reg4, reg5, type = "text", title = "Splitted hh. characteristics",digits=2,float = TRUE,se.position = "below", omit.stat=c("LL","ser","f","adj.rsq","res.dev"), dep.var.labels.include = TRUE,font.size="small",
          se.position = "below",notes.align = "l",table.placement = "H",header = F,
          column.labels = c("","Exposed UP.", "At least One", "Highly exposed", "Speed","Duration"),
          
          keep = c("hhm_sex" , "hhm_age", "hh_size" ,  "marital_status_hhm", "literacy_hhm", "education_high","hh_head_religion","hh_ethnic_group", "affected_upazila","high_exposed","exposed_at_least_zero","nbr_female", "nbr_underfive", "nbr_yngchldrn_5_10", "nbr_teenager_10_20", "nbr_adults_20_65", "nbr_female_underfive", "nbr_female_yngchldrn_5_10", "nbr_female_teenager_10_20", "nbr_female_adults_20_65"), notes = "Author's owns computations")

# ,
#           
#            covariate.labels = c("Hh. head sex", "Hh. head age","Hh. size", "Hh. head mrtl stts", "Hh. head ltrc" , "Hh. head edctn","Hh. head rlgn","Hh. head ethnc",
# "Affected upazila", "Hh. nbr fml" , "Hh. nbr undrfv" , "Hh. nbr yng child (5-10)" , "Hh. nbr tngr (10-20)", "Hh. nbr adlts (20-65)", "Hh. nbr female undrfv","Hh. fml yng child (5-10)", "Hh. fml tngr (10-20)","Hh. fml adlts (20-65)"),

```


```{r, results='hold', include = TRUE, warning=FALSE, echo = FALSE}
df_r1_hh %>% 
  mutate(hh_split_r2_r3 = ifelse(hh_split_r3=="1"| hh_split_r2=="1","1","0")) %>% 
  # Selecting relevant variables
   select(hh_split_r2_r3,interview_status_r2,interview_status_r3) %>% 
  
mutate(
        hh_split_r2_r3 = factor(hh_split_r2_r3, levels = c("0", "1"), labels = c("Don't split", "Split"), ordered = TRUE)) %>%
      # Generate a summary table using "tbl_summary" for the specified columns
    tbl_summary(
    by = hh_split_r2_r3, 
     label = list(
       interview_status_r2 ~ "Interview status in R2",
       interview_status_r3 ~ "Interview status R3"),
    
    #type = list(affected_upazila ~ "dichotomous"),
    statistic = list(
      all_categorical() ~ "{n} ({p}%)",
      all_continuous() ~ "{mean} ({sd})"
    ),
    missing_text = "(Missing)",
    digits = everything() ~ c(0,2),
    missing = "ifany"
  ) %>%
       add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) %>% 
  modify_header(label ~ "") %>% 
  add_overall(last=TRUE)
```

- How to correct ???

In the following, I remove the split households (from the initial 6503 households, I remove the 449 to perform the attrition analysis). Therefore 6054 hh remains



### Attrition

Interestingly, some households that migrated in R2 were found by enumerators and surveyed in R3: 65 among the 234 households who migrated between R1 and R2, around 27.78 percent.

My attrition is defined as the *households that were not surveyed in R3 (after the disaster)* because of:

- Migration: 5.71 percent (346/6054),
- Not at home when enumerators came: 0.4 percent (24/6054),
- Not found (total attrition): 16.17 percent (979/6054),
- Refused: 0.24 percent (15/6054).

Therefore a total attrition of 22.53 percent over 9 years (around 0.97 per year).

```{r, results='hold', include = TRUE, warning=FALSE, echo = FALSE}
df_r1_hh %>% 
  mutate(hh_split_r2_r3 = ifelse(hh_split_r3=="1"| hh_split_r2=="1","1","0")) %>% 
  # Selecting relevant variables
  filter(hh_split_r2_r3=="0") %>% 
   select(interview_status_r2,interview_status_r3) %>% 
      # Generate a summary table using "tbl_summary" for the specified columns
    tbl_summary(
    by = interview_status_r3, 
     label = list(
       interview_status_r2 ~ "Interview status in R2"),
    
    #type = list(affected_upazila ~ "dichotomous"),
    statistic = list(
      all_categorical() ~ "{n} ({p}%)",
      all_continuous() ~ "{mean} ({sd})"
    ),
    missing_text = "(Missing)",
    digits = everything() ~ c(0,2),
    missing = "ifany"
  ) %>%
       add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) %>% 
  modify_header(label ~ "Interview status in R3") %>% 
  add_overall(last=TRUE)
```

This figure summarize the idea of the previous table.

1177+187 = 1364 ==1364 from the previous table


```{r, results='hold', include = TRUE, warning=FALSE, echo = FALSE}

lst_menage <- df_r1_hh %>% 
  mutate(hh_split_r2_r3 = ifelse(hh_split_r3=="1"| hh_split_r2=="1","1","0")) %>% 
  filter(hh_split_r2_r3=="0") %>%  
  select(hh_id) %>% 
  pull()

all_comb <- df_r1_hh %>%
            select(hh_id,survey_round) %>% 
            filter(hh_id %in% lst_menage) %>% 
            plyr::rbind.fill(df_r2_hh %>%
            select(hh_id,survey_round)%>% 
            filter(hh_id %in% lst_menage)) %>% 
            plyr::rbind.fill(df_r3_hh %>%
            select(hh_id,survey_round)%>% 
            filter(hh_id %in% lst_menage)) %>% 
            tidyr::expand(hh_id,survey_round)

# Use with `right_join()` to fill in missing rows (in data)
all_comb <- df_r1_hh %>%
          select(hh_id,survey_round, hh_size, affected_upazila,treat_group, survey_year) %>% 
          filter(hh_id %in% lst_menage)%>% 
          plyr::rbind.fill(
            df_r2_hh %>%
              select(hh_id,survey_round, hh_size, affected_upazila,treat_group, survey_year)%>% 
          filter(hh_id %in% lst_menage))%>% 
          plyr::rbind.fill(
            df_r3_hh %>%
              select(hh_id,survey_round, hh_size, affected_upazila,treat_group, survey_year)%>% 
              filter(hh_id %in% lst_menage))%>% 
  dplyr::right_join(all_comb, by=c("survey_round", "hh_id")) %>% 
  mutate(
    survey_year = ifelse(survey_round==1,2011,
                              ifelse(survey_round==2,2015,
                                     ifelse(survey_round==3,2018,NA))))


# PanelView graph
panelView::panelview(1 ~ treat_group + hh_size, gridOff = TRUE, by.timing = TRUE,
          data = all_comb, index = c("hh_id","survey_year"), display.all = TRUE,
          xlab = "Survey year", ylab = "Nbr hh.", pre.post = TRUE, by.unit=TRUE,  background = "white",cex.main = 20, cex.axis= 8, cex.lab = 12, cex.legend = 12, collapse.history = "TRUE", main = "")
```




The attrited households are, on average:

- smaller in terms of size.
- have older heads.
- live in disaster-affected upazilas.
- have an Hindu household head.
- have a head who is Bengali.
- more likely to be male-headed.
- have unclear education and literacy levels.
- have fewer female members.
- have fewer teenagers.
- have fewer female teenagers.

I use R1 data to do these table
```{r, results='hold', include = TRUE, warning=FALSE, echo = FALSE}
# remove the splitted hh
df_r1_hh %>% 
  mutate(hh_split_r2_r3 = ifelse(hh_split_r3=="1"| hh_split_r2=="1","1","0"),
         attrition = ifelse(interview_status_r3=="Complete","0","1")) %>% 
  # Selecting relevant variables
  filter(hh_split_r2_r3=="0") %>% 
  # Selecting relevant variables
   select(hh_id,attrition,hh_size,affected_upazila,hh_head_religion,hh_ethnic_group) %>% 
  
mutate(affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE),
       attrition = factor(attrition, levels = c("0", "1"), labels = c("Hh. doesn't attrited", "Hh. attrited"), ordered = TRUE)) %>%
  left_join(
    df_r1_anthr1 %>% 
      filter(relation_hhh=="primary respondent") %>% 
      select(hh_id, hhm_sex, hhm_age, marital_status_hhm, literacy_hhm, education_high, hhm_status, nbr_female, nbr_underfive, nbr_yngchldrn_5_10, nbr_teenager_10_20, nbr_adults_20_65, nbr_female_underfive, nbr_female_yngchldrn_5_10, nbr_female_teenager_10_20, nbr_female_adults_20_65)) %>% 
mutate(
         nbr_female = as.numeric(nbr_female),
         nbr_underfive = as.numeric(nbr_underfive),
         nbr_yngchldrn_5_10 = as.numeric(nbr_yngchldrn_5_10),
         nbr_teenager_10_20 = as.numeric(nbr_teenager_10_20),
         nbr_adults_20_65 = as.numeric(nbr_adults_20_65),
         nbr_female_underfive = as.numeric(nbr_female_underfive),
         nbr_female_yngchldrn_5_10 = as.numeric(nbr_female_yngchldrn_5_10),
         nbr_female_teenager_10_20 = as.numeric(nbr_female_teenager_10_20),
         nbr_female_adults_20_65 = as.numeric(nbr_female_adults_20_65)) %>%
  select(-c(hh_id)) %>% 
  
  
  
      # Generate a summary table using "tbl_summary" for the specified columns
    tbl_summary(
    by = attrition, 
     label = list(
       hh_size ~ "Hh. size",
       hh_head_religion ~ "Hh. head rlgn",
       hh_ethnic_group  ~ "Hh. head ethnc",
       affected_upazila ~ "Affected upazila",
       hhm_sex ~ "Hh. head sex", 
       hhm_age ~ "Hh. head age", 
       marital_status_hhm ~ "Hh. head mrtl stts", 
       literacy_hhm ~ "Hh. head ltrc" , 
       education_high ~ "Hh. head edctn", 
       hhm_status ~ "Hh. head stts",
       nbr_female ~ "Hh. nbr fml" , 
       nbr_underfive ~ "Hh. nbr undrfv" , 
       nbr_yngchldrn_5_10 ~ "Hh. nbr yng child (5-10)" , 
       nbr_teenager_10_20 ~ "Hh. nbr tngr (10-20)", 
       nbr_adults_20_65 ~ "Hh. nbr adlts (20-65)", 
       nbr_female_underfive ~ "Hh. nbr female undrfv", 
       nbr_female_yngchldrn_5_10 ~ "Hh. fml yng child (5-10)", 
       nbr_female_teenager_10_20 ~ "Hh. fml tngr (10-20)",
       nbr_female_adults_20_65 ~ "Hh. fml adlts (20-65)"),
    
    type = list(
       nbr_female ~ "continuous" , 
       nbr_underfive ~ "continuous" , 
       nbr_yngchldrn_5_10 ~ "continuous" , 
       nbr_teenager_10_20 ~ "continuous", 
       nbr_adults_20_65 ~ "continuous", 
       nbr_female_underfive ~ "continuous", 
       nbr_female_yngchldrn_5_10 ~ "continuous", 
       nbr_female_teenager_10_20 ~ "continuous",
       nbr_female_adults_20_65 ~ "continuous"
      ),
    statistic = list(
      all_categorical() ~ "{n} ({p}%)",
      all_continuous() ~ "{mean} ({sd})"
    ),
    missing_text = "(Missing)",
    digits = list(all_continuous() ~ c(2,2)),
    missing = "ifany"
  ) %>%
       add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) %>% 
  modify_header(label ~ "") %>% 
  add_overall(last=TRUE)
```


```{r, results='hold', include = TRUE, warning=FALSE, echo = FALSE}
df_reg = df_r1_hh %>% 
  mutate(hh_split_r2_r3 = ifelse(hh_split_r3=="1"| hh_split_r2=="1","1","0"),
         attrition = ifelse(interview_status_r3=="Complete","0","1")) %>% 
  # Selecting relevant variables
  filter(hh_split_r2_r3=="0") %>%  
  # Selecting relevant variables
   select(hh_id, attrition,hh_size,affected_upazila,hh_head_religion,hh_ethnic_group) %>% 
  left_join(
    df_r1_anthr1 %>% 
      filter(relation_hhh=="primary respondent") %>% 
      select(hh_id, hhm_sex, hhm_age, marital_status_hhm, literacy_hhm, education_high, hhm_status, nbr_female, nbr_underfive, nbr_yngchldrn_5_10, nbr_teenager_10_20, nbr_adults_20_65, nbr_female_underfive, nbr_female_yngchldrn_5_10, nbr_female_teenager_10_20, nbr_female_adults_20_65, high_exposed, exposed_at_least_zero)) %>% 
mutate(
  high_exposed = factor(high_exposed, levels = c("0", "1")),
  exposed_at_least_zero = factor(exposed_at_least_zero, levels = c("0", "1")),
  affected_upazila = factor(affected_upazila, levels = c("0", "1")),
         nbr_female = as.numeric(nbr_female),
         nbr_underfive = as.numeric(nbr_underfive),
         nbr_yngchldrn_5_10 = as.numeric(nbr_yngchldrn_5_10),
         nbr_teenager_10_20 = as.numeric(nbr_teenager_10_20),
         nbr_adults_20_65 = as.numeric(nbr_adults_20_65),
         nbr_female_underfive = as.numeric(nbr_female_underfive),
         nbr_female_yngchldrn_5_10 = as.numeric(nbr_female_yngchldrn_5_10),
         nbr_female_teenager_10_20 = as.numeric(nbr_female_teenager_10_20),
         nbr_female_adults_20_65 = as.numeric(nbr_female_adults_20_65)) %>%
  select(-c(hh_id))

#stargazer(regsplit,  type = "text", title = "Split and household characteristics")

reg_1 <- felm(attrition ~ hhm_sex + hhm_age+ hh_size +  marital_status_hhm+ literacy_hhm+ education_high +  hh_head_religion + hh_ethnic_group + affected_upazila + nbr_female+ nbr_underfive+ nbr_yngchldrn_5_10+ nbr_teenager_10_20+ nbr_adults_20_65+ nbr_female_underfive+ nbr_female_yngchldrn_5_10+ nbr_female_teenager_10_20+ nbr_female_adults_20_65, data=df_reg)

reg_2 <- felm(attrition ~ hhm_sex + hhm_age+ hh_size +  marital_status_hhm+ literacy_hhm+ education_high +  hh_head_religion + hh_ethnic_group + high_exposed + nbr_female+ nbr_underfive+ nbr_yngchldrn_5_10+ nbr_teenager_10_20+ nbr_adults_20_65+ nbr_female_underfive+ nbr_female_yngchldrn_5_10+ nbr_female_teenager_10_20+ nbr_female_adults_20_65, data=df_reg)

reg_3 <- felm(attrition ~ hhm_sex + hhm_age+ hh_size +  marital_status_hhm+ literacy_hhm+ education_high +  hh_head_religion + hh_ethnic_group + exposed_at_least_zero + nbr_female+ nbr_underfive+ nbr_yngchldrn_5_10+ nbr_teenager_10_20+ nbr_adults_20_65+ nbr_female_underfive+ nbr_female_yngchldrn_5_10+ nbr_female_teenager_10_20+ nbr_female_adults_20_65, data=df_reg)


stargazer(reg_1, reg_2, reg_3, type = "text", title = "Attrited hh. characteristics", digits=2, float = TRUE,se.position = "below", omit.stat=c("LL","ser","f","adj.rsq","res.dev"), dep.var.labels.include = TRUE,font.size="small",
          se.position = "below",notes.align = "l",table.placement = "H",header = F,
          column.labels = c("Binary for splitted hh."),
          
          keep = c("hhm_sex" , "hhm_age", "hh_size" ,  "marital_status_hhm", "literacy_hhm", "education_high","hh_head_religion","hh_ethnic_group", "affected_upazila","high_exposed","exposed_at_least_zero","nbr_female", "nbr_underfive", "nbr_yngchldrn_5_10", "nbr_teenager_10_20", "nbr_adults_20_65", "nbr_female_underfive", "nbr_female_yngchldrn_5_10", "nbr_female_teenager_10_20", "nbr_female_adults_20_65"), notes = "Author's owns computations")


```


### Individual level analysis

#### All hh members

In the following, I restrict the sample to the households that do not split and do not attrite in the following round of the survey.

Non-affected individuals are on average:

* bigger, but the difference is not statistically significant
* taller
* more likely to be married and less likely to have never been married
* more likely to read
```{r, results='hold', include = TRUE, warning=FALSE, echo = FALSE}

lst_menage <- df_r1_hh %>% 
  mutate(hh_split_r2_r3 = ifelse(hh_split_r3=="1"| hh_split_r2=="1","1","0"), attrition = ifelse(interview_status_r3=="Complete","0","1")) %>% 
  filter(hh_split_r2_r3=="0") %>%  
  filter(attrition=="0") %>% 
  dplyr::select(hh_id) %>% 
  pull()

# Table 1
df_global %>% 
  filter(hh_id %in% lst_menage) %>%
  select(weight_kg,height_cm,hhm_sex,hhm_age,relation_hhh,marital_status_hhm,literacy_hhm,education_high,hh_head_religion,hh_ethnic_group, affected_upazila, waz_who, haz_who, bmiz_who) %>% 
  mutate(affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE),
         hhm_age = as.numeric(hhm_age)) %>%
      # Generate a summary table using "tbl_summary" for the specified columns
    tbl_summary(
    by = affected_upazila, 
     label = list(
       hh_head_religion ~ "Religion",
       hh_ethnic_group  ~ "Ethnc",
       relation_hhh~"Relation with head",
       weight_kg ~ "Weight (kg)",
       height_cm ~ "Height (cm)",
      # affected_upazila ~ "Affected upazila",
       hhm_sex ~ "Sex", 
       hhm_age ~ "Age", 
       marital_status_hhm ~ "Marital status", 
       literacy_hhm ~ "Literacy" , 
       education_high ~ "Education",
       waz_who ~ "WAZ", 
       haz_who ~ "HAZ", 
       bmiz_who ~ "BMIZ"),
    
    type = list(
       hhm_age ~ "continuous" 
      ),
    statistic = list(
      all_categorical() ~ "{n} ({p}%)",
      all_continuous() ~ "{mean} ({sd})"
    ),
    missing_text = "(Missing)",
    digits = list(all_continuous() ~ c(2,2)),
    missing = "ifany"
  ) %>%
       add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) %>% 
  modify_header(label ~ "Affected Upazila") %>% 
  add_overall(last=TRUE)

# Table 2
df_global %>% 
  filter(hh_id %in% lst_menage) %>%
  select(weight_kg,height_cm,hhm_sex,hhm_age,relation_hhh,marital_status_hhm,literacy_hhm,education_high,hh_head_religion,hh_ethnic_group, high_exposed, waz_who, haz_who, bmiz_who) %>% 
  mutate(high_exposed = factor(high_exposed, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE),
         hhm_age = as.numeric(hhm_age)) %>%
      # Generate a summary table using "tbl_summary" for the specified columns
    tbl_summary(
    by = high_exposed, 
     label = list(
       hh_head_religion ~ "Religion",
       hh_ethnic_group  ~ "Ethnc",
       relation_hhh~"Relation with head",
       weight_kg ~ "Weight (kg)",
       height_cm ~ "Height (cm)",
      # affected_upazila ~ "Affected upazila",
       hhm_sex ~ "Sex", 
       hhm_age ~ "Age", 
       marital_status_hhm ~ "Marital status", 
       literacy_hhm ~ "Literacy" , 
       education_high ~ "Education",
       waz_who ~ "WAZ", 
       haz_who ~ "HAZ", 
       bmiz_who ~ "BMIZ"),
    
    type = list(
       hhm_age ~ "continuous" 
      ),
    statistic = list(
      all_categorical() ~ "{n} ({p}%)",
      all_continuous() ~ "{mean} ({sd})"
    ),
    missing_text = "(Missing)",
    digits = list(all_continuous() ~ c(2,2)),
    missing = "ifany"
  ) %>%
       add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) %>% 
  modify_header(label ~ "Highly Affected Union") %>% 
  add_overall(last=TRUE)


# Table 3
df_global %>% 
  filter(hh_id %in% lst_menage) %>%
  select(weight_kg,height_cm,hhm_sex,hhm_age,relation_hhh,marital_status_hhm,literacy_hhm,education_high,hh_head_religion,hh_ethnic_group, exposed_at_least_zero, waz_who, haz_who, bmiz_who) %>% 
  mutate(exposed_at_least_zero = factor(exposed_at_least_zero, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE),
         hhm_age = as.numeric(hhm_age)) %>%
      # Generate a summary table using "tbl_summary" for the specified columns
    tbl_summary(
    by = exposed_at_least_zero, 
     label = list(
       hh_head_religion ~ "Religion",
       hh_ethnic_group  ~ "Ethnc",
       relation_hhh~"Relation with head",
       weight_kg ~ "Weight (kg)",
       height_cm ~ "Height (cm)",
      # affected_upazila ~ "Affected upazila",
       hhm_sex ~ "Sex", 
       hhm_age ~ "Age", 
       marital_status_hhm ~ "Marital status", 
       literacy_hhm ~ "Literacy" , 
       education_high ~ "Education",
       waz_who ~ "WAZ", 
       haz_who ~ "HAZ", 
       bmiz_who ~ "BMIZ"),
    
    type = list(
       hhm_age ~ "continuous" 
      ),
    statistic = list(
      all_categorical() ~ "{n} ({p}%)",
      all_continuous() ~ "{mean} ({sd})"
    ),
    missing_text = "(Missing)",
    digits = list(all_continuous() ~ c(2,2)),
    missing = "ifany"
  ) %>%
       add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) %>% 
  modify_header(label ~ "Affected Union") %>% 
  add_overall(last=TRUE)
```
Missing data in the outcome variables (or components of them) at the individual level can come from several sources. Affected individuals are more likely to provide missing information because of:

* Absence (88% vs 86%) and refusal to answer (4.7% vs 2.2%)

```{r}
df_global %>% 
  filter(hh_id %in% lst_menage) %>%
  filter(if_not_measured_why!="have measured") %>% 
  select(if_not_measured_why, affected_upazila) %>% 
  mutate(affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE)) %>%
      # Generate a summary table using "tbl_summary" for the specified columns
    tbl_summary(
    by = affected_upazila, 
     label = list(
       if_not_measured_why  ~ "Reason for being missing in outcome"),
    
    #type = list(
       #hhm_age ~ "continuous" 
      #),
    statistic = list(
      all_categorical() ~ "{n} ({p}%)",
      all_continuous() ~ "{mean} ({sd})"
    ),
    missing_text = "(Missing)",
    digits = list(all_continuous() ~ c(2,2)),
    missing = "ifany"
  ) %>%
       add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) %>% 
  modify_header(label ~ "") %>% 
  add_overall(last=TRUE)
```
This table presents a regression analysis to identify factors that may explain why some individuals have NaN values in their outcome variables. It shows that the probability of being missing increases with:

* Being in a cyclone-affected upazila (possibly due to sickness)
* Being male (probably because they are more likely to be absent)
* Age
* Household size (the larger the household, the more likely there is an individual with missing)
* Literacy and having a diploma are negatively correlated with the probability of being missing



```{r, results='hold', include = TRUE, warning=FALSE, echo = FALSE}
df_reg <- df_global %>% 
  filter(hh_id %in% lst_menage) %>%
  # Selecting relevant variables
  mutate(out_missing = ifelse(if_not_measured_why=="have measured",0,1)) %>% 
  mutate(time_bin = as.factor(ifelse(survey_year>=2018,1,0)),
         affected_upazila = as.factor(affected_upazila))

#stargazer(regsplit,  type = "text", title = "Split and household characteristics")

regnan_1 <- felm(out_missing ~ affected_upazila*time_bin, data=df_reg)

regnan_2 <- felm(out_missing ~ affected_upazila*time_bin + hhm_sex + hhm_age +  marital_status_hhm + hh_size + literacy_hhm + education_high +  hh_head_religion + hh_ethnic_group + relation_hhh + affected_upazila + nbr_female+ nbr_underfive+ nbr_yngchldrn_5_10 + nbr_teenager_10_20+ nbr_adults_20_65+ nbr_female_underfive+ nbr_female_yngchldrn_5_10 + nbr_female_teenager_10_20 + nbr_female_adults_20_65, data=df_reg)

regnan_3 <- felm(out_missing ~ affected_upazila*time_bin + hhm_sex + hhm_age + marital_status_hhm + hh_size + literacy_hhm + education_high +  hh_head_religion + hh_ethnic_group + relation_hhh + affected_upazila + nbr_female+ nbr_underfive+ nbr_yngchldrn_5_10 + nbr_teenager_10_20+ nbr_adults_20_65+ nbr_female_underfive+ nbr_female_yngchldrn_5_10 + nbr_female_teenager_10_20 + nbr_female_adults_20_65|0|0|affected_upazila, data=df_reg)



stargazer(regnan_1, regnan_2,regnan_3, type = "text", title = "Prob. of missing", digits=2, float = TRUE,se.position = "below", omit.stat=c("LL","ser","f","adj.rsq","res.dev"), dep.var.labels.include = TRUE,font.size="small",
          se.position = "below",notes.align = "l",table.placement = "H",header = F,
          column.labels = c("Binary for missing"),
          
          keep = c("affected_upazila","time_bin","affected_upazila:time_bin","hhm_sex" , "hhm_age", "hh_size" ,  "marital_status_hhm", "literacy_hhm", "education_high","hh_head_religion","hh_ethnic_group", "affected_upazila","nbr_female", "nbr_underfive", "nbr_yngchldrn_5_10", "nbr_teenager_10_20", "nbr_adults_20_65", "nbr_female_underfive", "nbr_female_yngchldrn_5_10", "nbr_female_teenager_10_20", "nbr_female_adults_20_65"), notes = "Author's owns computations")


# Highly affected 

regnan_1 <- felm(out_missing ~ high_exposed*time_bin, data=df_reg)

regnan_2 <- felm(out_missing ~ high_exposed*time_bin + hhm_sex + hhm_age +  marital_status_hhm + hh_size + literacy_hhm + education_high +  hh_head_religion + hh_ethnic_group + relation_hhh + affected_upazila + nbr_female+ nbr_underfive+ nbr_yngchldrn_5_10 + nbr_teenager_10_20+ nbr_adults_20_65+ nbr_female_underfive+ nbr_female_yngchldrn_5_10 + nbr_female_teenager_10_20 + nbr_female_adults_20_65, data=df_reg)

regnan_3 <- felm(out_missing ~ high_exposed*time_bin + hhm_sex + hhm_age + marital_status_hhm + hh_size + literacy_hhm + education_high +  hh_head_religion + hh_ethnic_group + relation_hhh + affected_upazila + nbr_female+ nbr_underfive+ nbr_yngchldrn_5_10 + nbr_teenager_10_20+ nbr_adults_20_65+ nbr_female_underfive+ nbr_female_yngchldrn_5_10 + nbr_female_teenager_10_20 + nbr_female_adults_20_65|0|0|high_exposed, data=df_reg)



stargazer(regnan_1, regnan_2,regnan_3, type = "text", title = "Prob. of missing", digits=2, float = TRUE,se.position = "below", omit.stat=c("LL","ser","f","adj.rsq","res.dev"), dep.var.labels.include = TRUE,font.size="small",
          se.position = "below",notes.align = "l",table.placement = "H",header = F,
          column.labels = c("Binary for missing"),
          keep = c("high_exposed","time_bin","high_exposed:time_bin","hhm_sex" , "hhm_age", "hh_size" ,  "marital_status_hhm", "literacy_hhm", "education_high","hh_head_religion","hh_ethnic_group", "high_exposed","nbr_female", "nbr_underfive", "nbr_yngchldrn_5_10", "nbr_teenager_10_20", "nbr_adults_20_65", "nbr_female_underfive", "nbr_female_yngchldrn_5_10", "nbr_female_teenager_10_20", "nbr_female_adults_20_65"), notes = "Author's owns computations")


# Affected union

regnan_1 <- felm(out_missing ~ exposed_at_least_zero*time_bin, data=df_reg)

regnan_2 <- felm(out_missing ~ exposed_at_least_zero*time_bin + hhm_sex + hhm_age +  marital_status_hhm + hh_size + literacy_hhm + education_high +  hh_head_religion + hh_ethnic_group + relation_hhh + affected_upazila + nbr_female+ nbr_underfive+ nbr_yngchldrn_5_10 + nbr_teenager_10_20+ nbr_adults_20_65+ nbr_female_underfive+ nbr_female_yngchldrn_5_10 + nbr_female_teenager_10_20 + nbr_female_adults_20_65, data=df_reg)

regnan_3 <- felm(out_missing ~ exposed_at_least_zero*time_bin + hhm_sex + hhm_age + marital_status_hhm + hh_size + literacy_hhm + education_high +  hh_head_religion + hh_ethnic_group + relation_hhh + affected_upazila + nbr_female+ nbr_underfive+ nbr_yngchldrn_5_10 + nbr_teenager_10_20+ nbr_adults_20_65+ nbr_female_underfive+ nbr_female_yngchldrn_5_10 + nbr_female_teenager_10_20 + nbr_female_adults_20_65|0|0|exposed_at_least_zero, data=df_reg)



stargazer(regnan_1, regnan_2,regnan_3, type = "text", title = "Prob. of missing", digits=2, float = TRUE,se.position = "below", omit.stat=c("LL","ser","f","adj.rsq","res.dev"), dep.var.labels.include = TRUE,font.size="small",
          se.position = "below",notes.align = "l",table.placement = "H",header = F,
          column.labels = c("Binary for missing"),
          keep = c("exposed_at_least_zero","time_bin","exposed_at_least_zero:time_bin","hhm_sex" , "hhm_age", "hh_size" ,  "marital_status_hhm", "literacy_hhm", "education_high","hh_head_religion","hh_ethnic_group", "exposed_at_least_zero","nbr_female", "nbr_underfive", "nbr_yngchldrn_5_10", "nbr_teenager_10_20", "nbr_adults_20_65", "nbr_female_underfive", "nbr_female_yngchldrn_5_10", "nbr_female_teenager_10_20", "nbr_female_adults_20_65"), notes = "Author's owns computations")


```


Affected household seems to have more new member than non affected household.


```{r}
# Table 1
df_global %>% 
  filter(hh_id %in% lst_menage) %>%
  select(hhm_status, affected_upazila) %>% 
  mutate(affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE)) %>%
      # Generate a summary table using "tbl_summary" for the specified columns
    tbl_summary(
    by = affected_upazila, 
     label = list(
       hhm_status  ~ "Member status"),
    
    #type = list(
       #hhm_age ~ "continuous" 
      #),
    statistic = list(
      all_categorical() ~ "{n} ({p}%)",
      all_continuous() ~ "{mean} ({sd})"
    ),
    missing_text = "(Missing)",
    digits = list(all_continuous() ~ c(2,2)),
    missing = "ifany"
  ) %>%
       add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) %>% 
  modify_header(label ~ "Affected Upazila") %>% 
  add_overall(last=TRUE)

# Table 2
df_global %>% 
  filter(hh_id %in% lst_menage) %>%
  select(hhm_status, high_exposed) %>% 
  mutate(high_exposed = factor(high_exposed, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE)) %>%
      # Generate a summary table using "tbl_summary" for the specified columns
    tbl_summary(
    by = high_exposed, 
     label = list(
       hhm_status  ~ "Member status"),
    
    #type = list(
       #hhm_age ~ "continuous" 
      #),
    statistic = list(
      all_categorical() ~ "{n} ({p}%)",
      all_continuous() ~ "{mean} ({sd})"
    ),
    missing_text = "(Missing)",
    digits = list(all_continuous() ~ c(2,2)),
    missing = "ifany"
  ) %>%
       add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) %>% 
  modify_header(label ~ "Highly Affected Union") %>% 
  add_overall(last=TRUE)

# Table 3
df_global %>% 
  filter(hh_id %in% lst_menage) %>%
  select(hhm_status, exposed_at_least_zero) %>% 
  mutate(exposed_at_least_zero = factor(exposed_at_least_zero, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE)) %>%
      # Generate a summary table using "tbl_summary" for the specified columns
    tbl_summary(
    by = exposed_at_least_zero, 
     label = list(
       hhm_status  ~ "Member status"),
    
    #type = list(
       #hhm_age ~ "continuous" 
      #),
    statistic = list(
      all_categorical() ~ "{n} ({p}%)",
      all_continuous() ~ "{mean} ({sd})"
    ),
    missing_text = "(Missing)",
    digits = list(all_continuous() ~ c(2,2)),
    missing = "ifany"
  ) %>%
       add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) %>% 
  modify_header(label ~ "Affected Union") %>% 
  add_overall(last=TRUE)
```



The following table summarizes each household member's history during the second and third survey rounds, depending on their status during the first survey round:

* Among the members in the first round:
  - N = 19298 (77.6 percent) were permanent household members during the first round;
  - N = 3094 (12.4 percent) individuals joined the household later for reasons not related to birth;
    - N = 2473 (10 percent) children were unborn during the first round but joined the household later (during r2 or r3);
  - N = 3 (<1 percent) are unsure or missing.




```{r, results='hold', include = TRUE, warning=FALSE, echo = FALSE}

# niveau individus
lst_menage <- df_r1_hh %>% 
  mutate(hh_split_r2_r3 = ifelse(hh_split_r3=="1"| hh_split_r2=="1","1","0"),
         attrition = ifelse(interview_status_r3=="Complete","0","1")) %>% 
  filter(hh_split_r2_r3=="0") %>%  
  filter(attrition=="0") %>% 
  dplyr::select(hh_id) %>% 
  pull()

lst_later_join = c('New member through marriage','New member upon return from divorce or seperation','Household merged/combined','Other reasons (permanent)','Residing elsewhere for the pursuit of studies')

#'Death','Married and left household','Divorced and left household','Household split','Left household for employment','Other reasns for leaving the household','New sample household and current round member'

tbl_data <- df_r2_anthr1 %>% 
  filter(hh_id %in% lst_menage) %>% 
  select(member_id, hhm_status) %>% 
  rename(hhm_status_r2 = hhm_status) %>%
  plyr::rbind.fill(
    df_r2_anthr2 %>% 
      filter(hh_id %in% lst_menage) %>% 
      select(member_id, hhm_status) %>% 
      rename(hhm_status_r2 = hhm_status)) %>% 
  dplyr::full_join(
    df_r3_anthr1 %>% 
      filter(hh_id %in% lst_menage) %>% 
      select(member_id, hhm_status) %>% 
      rename(hhm_status_r3 = hhm_status) %>%
    plyr::rbind.fill(
      df_r3_anthr2 %>% 
        filter(hh_id %in% lst_menage) %>% 
        select(member_id, hhm_status) %>% 
        rename(hhm_status_r3 = hhm_status))) %>% 
  dplyr::full_join(
    df_r1_anthr1 %>% 
      filter(hh_id %in% lst_menage) %>% 
      select(member_id, hhm_status) %>% 
      rename(hhm_status_r1 = hhm_status) %>%
    plyr::rbind.fill(
      df_r1_anthr2 %>% 
        filter(hh_id %in% lst_menage) %>% 
        select(member_id, hhm_status) %>% 
        rename(hhm_status_r1 = hhm_status))) %>% 
  select(member_id, hhm_status_r1, hhm_status_r2, hhm_status_r3) %>% 
  mutate(hhm_status_r2 = ifelse(is.na(hhm_status_r1) & is.na(hhm_status_r2) & (hhm_status_r3 == "New member (new born)"),"Unborn", ifelse(is.na(hhm_status_r1) & is.na(hhm_status_r2) & (hhm_status_r3 %in% lst_later_join),"Join later",hhm_status_r2)),
         
hhm_status_r1 = ifelse(is.na(hhm_status_r1) & (hhm_status_r2 == "New member (new born)"),"Unborn",ifelse(is.na(hhm_status_r1) & (hhm_status_r2 %in% c(lst_later_join, "Join later")),"Join later",ifelse(is.na(hhm_status_r1) & (hhm_status_r2 == "Unborn"),"Unborn",  hhm_status_r1))))

tbl_data <- tbl_data %>% 
  mutate(hhm_status_r1 = replace_na(hhm_status_r1, "Missing"),
         hhm_status_r2 = replace_na(hhm_status_r2, "Missing"),
         hhm_status_r3 = replace_na(hhm_status_r3, "Missing"))

tbl_data %>% 
  select(hhm_status_r1, hhm_status_r2, hhm_status_r3) %>% 
  tbl_strata(
    strata = hhm_status_r1,
    .tbl_fun =
      ~ .x %>%
      tbl_summary(
    by = hhm_status_r3, 
      label = list(
        hhm_status_r3 ~ "Status R3",
        hhm_status_r2 ~ "Status R2"
     ),
    statistic = list(
      all_categorical() ~ "{n} ({p}%)",
      all_continuous() ~ "{mean} ({sd})"
    ),
    missing_text = "(Missing)",
    digits = everything() ~ c(0,2),
    missing = "ifany"
  ) %>%
      add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) %>%
      # Modify the table header to provide a descriptive label
      modify_header(label ~ "Member status in R2 vs R3"),
    # Add difference statistics to the table
    #add_difference(),
    .header = "**{strata}**, N = {n}",
    #.combine_with = "tbl_stack",
    #.combine_args = list(group_header = NULL),
    .quiet = TRUE) 
```

There is 578 individuals with always NaN values for the three survey round. Among these we have people that are always sick or absent or even born during the last round but with NaN values in it.


```{r results='hold', include = TRUE, warning=FALSE, echo = FALSE}

# niveau individus
lst_menage <- df_r1_hh %>% 
  mutate(hh_split_r2_r3 = ifelse(hh_split_r3=="1"| hh_split_r2=="1","1","0"),
         attrition = ifelse(interview_status_r3=="Complete","0","1")) %>% 
  filter(hh_split_r2_r3=="0") %>%  
  filter(attrition=="0") %>% 
  dplyr::select(hh_id) %>% 
  pull()

all_comb <- df_global %>%
            select(hh_id, member_id, survey_year) %>% 
            filter(hh_id %in% lst_menage) %>% 
            tidyr::expand(member_id,survey_year)

# Use with `right_join()` to fill in missing rows (in data)
all_comb <- df_global %>%
            select(hh_id, member_id, survey_year, affected_upazila, treat_group, weight_kg, hhm_age, if_not_measured_why) %>% 
            filter(hh_id %in% lst_menage) %>% 
  dplyr::right_join(all_comb, by=c("member_id","survey_year")) %>% 
  mutate(treat_group = ifelse((survey_year < 2018) & (is.na(treat_group)),0, treat_group))

lst_treat_people <- all_comb %>% filter(treat_group==1) %>% select(member_id) %>% distinct() %>% pull()

all_comb <- all_comb %>% 
  mutate(treat_group = ifelse((survey_year == 2018) & (is.na(treat_group)) & (member_id %in% lst_treat_people),1, ifelse( (survey_year == 2018) & (is.na(treat_group)) & !(member_id %in% lst_treat_people),0, treat_group)))

panelView::panelview(1 ~ treat_group + weight_kg, gridOff = TRUE, by.timing = TRUE, data = all_comb, index = c("member_id","survey_year"), display.all = TRUE,
          xlab = "Year", ylab = "Nbr individuals", pre.post = TRUE, by.unit=TRUE,  background = "white",cex.main = 20, cex.axis= 8, cex.lab = 12, cex.legend = 12, collapse.history = "TRUE", main = "")

```

Now, I would like to understand the factors that can explain the probability of being missing after the disaster (the attrition at the individual level). I ran a regression after the disaster to understand the characteristics that can explain the probability of being missing. I found that the same factors from the previous analysis explain the probability of being missing.




```{r, results='hold', include = TRUE, warning=FALSE, echo = FALSE}
df_reg <- df_global %>% 
  filter(hh_id %in% lst_menage) %>%
  filter(survey_round==3) %>% 
  # Selecting relevant variables
  mutate(out_missing = ifelse(if_not_measured_why=="have measured",0,1)) %>% 
  mutate(time_bin = as.factor(ifelse(survey_year>=2018,1,0)),
         affected_upazila = as.factor(affected_upazila))

#stargazer(regsplit,  type = "text", title = "Split and household characteristics")

regnan_1 <- felm(out_missing ~ affected_upazila, data=df_reg)

regnan_2 <- felm(out_missing ~ affected_upazila + hhm_sex + hhm_age +  marital_status_hhm + hh_size + literacy_hhm + education_high +  hh_head_religion + hh_ethnic_group + relation_hhh  + nbr_female+ nbr_underfive+ nbr_yngchldrn_5_10 + nbr_teenager_10_20+ nbr_adults_20_65+ nbr_female_underfive+ nbr_female_yngchldrn_5_10 + nbr_female_teenager_10_20 + nbr_female_adults_20_65, data=df_reg)

regnan_3 <- felm(out_missing ~ affected_upazila + hhm_sex + hhm_age + marital_status_hhm + hh_size + literacy_hhm + education_high +  hh_head_religion + hh_ethnic_group + relation_hhh + nbr_female+ nbr_underfive+ nbr_yngchldrn_5_10 + nbr_teenager_10_20+ nbr_adults_20_65+ nbr_female_underfive+ nbr_female_yngchldrn_5_10 + nbr_female_teenager_10_20 + nbr_female_adults_20_65|0|0|affected_upazila, data=df_reg)



stargazer(regnan_1, regnan_2,regnan_3, type = "text", title = "Prob. of missing", digits=2, float = TRUE,se.position = "below", omit.stat=c("LL","ser","f","adj.rsq","res.dev"), dep.var.labels.include = TRUE,font.size="small",
          se.position = "below",notes.align = "l",table.placement = "H",header = F,
          column.labels = c("Binary for missing"),
          
          keep = c("affected_upazila","hhm_sex" , "hhm_age", "hh_size" ,  "marital_status_hhm", "literacy_hhm", "education_high","hh_head_religion","hh_ethnic_group", "affected_upazila","nbr_female", "nbr_underfive", "nbr_yngchldrn_5_10", "nbr_teenager_10_20", "nbr_adults_20_65", "nbr_female_underfive", "nbr_female_yngchldrn_5_10", "nbr_female_teenager_10_20", "nbr_female_adults_20_65"), notes = "Author's owns computations")



# Table 2

regnan_1 <- felm(out_missing ~ high_exposed, data=df_reg)

regnan_2 <- felm(out_missing ~ high_exposed + hhm_sex + hhm_age +  marital_status_hhm + hh_size + literacy_hhm + education_high +  hh_head_religion + hh_ethnic_group + relation_hhh + nbr_female+ nbr_underfive+ nbr_yngchldrn_5_10 + nbr_teenager_10_20+ nbr_adults_20_65+ nbr_female_underfive+ nbr_female_yngchldrn_5_10 + nbr_female_teenager_10_20 + nbr_female_adults_20_65, data=df_reg)

regnan_3 <- felm(out_missing ~ high_exposed + hhm_sex + hhm_age + marital_status_hhm + hh_size + literacy_hhm + education_high +  hh_head_religion + hh_ethnic_group + relation_hhh + affected_upazila + nbr_female+ nbr_underfive+ nbr_yngchldrn_5_10 + nbr_teenager_10_20+ nbr_adults_20_65+ nbr_female_underfive+ nbr_female_yngchldrn_5_10 + nbr_female_teenager_10_20 + nbr_female_adults_20_65|0|0|high_exposed, data=df_reg)



stargazer(regnan_1, regnan_2,regnan_3, type = "text", title = "Prob. of missing", digits=2, float = TRUE,se.position = "below", omit.stat=c("LL","ser","f","adj.rsq","res.dev"), dep.var.labels.include = TRUE,font.size="small",
          se.position = "below",notes.align = "l",table.placement = "H",header = F,
          column.labels = c("Binary for missing"),
          
          keep = c("high_exposed","hhm_sex" , "hhm_age", "hh_size" ,  "marital_status_hhm", "literacy_hhm", "education_high","hh_head_religion","hh_ethnic_group", "nbr_female", "nbr_underfive", "nbr_yngchldrn_5_10", "nbr_teenager_10_20", "nbr_adults_20_65", "nbr_female_underfive", "nbr_female_yngchldrn_5_10", "nbr_female_teenager_10_20", "nbr_female_adults_20_65"), notes = "Author's owns computations")


# Table 3
regnan_1 <- felm(out_missing ~ exposed_at_least_zero, data=df_reg)

regnan_2 <- felm(out_missing ~ exposed_at_least_zero + hhm_sex + hhm_age +  marital_status_hhm + hh_size + literacy_hhm + education_high +  hh_head_religion + hh_ethnic_group + relation_hhh + nbr_female+ nbr_underfive+ nbr_yngchldrn_5_10 + nbr_teenager_10_20+ nbr_adults_20_65+ nbr_female_underfive+ nbr_female_yngchldrn_5_10 + nbr_female_teenager_10_20 + nbr_female_adults_20_65, data=df_reg)

regnan_3 <- felm(out_missing ~ exposed_at_least_zero + hhm_sex + hhm_age + marital_status_hhm + hh_size + literacy_hhm + education_high +  hh_head_religion + hh_ethnic_group + relation_hhh + affected_upazila + nbr_female+ nbr_underfive+ nbr_yngchldrn_5_10 + nbr_teenager_10_20+ nbr_adults_20_65+ nbr_female_underfive+ nbr_female_yngchldrn_5_10 + nbr_female_teenager_10_20 + nbr_female_adults_20_65|0|0|exposed_at_least_zero, data=df_reg)



stargazer(regnan_1, regnan_2,regnan_3, type = "text", title = "Prob. of missing", digits=2, float = TRUE,se.position = "below", omit.stat=c("LL","ser","f","adj.rsq","res.dev"), dep.var.labels.include = TRUE,font.size="small",
          se.position = "below",notes.align = "l",table.placement = "H",header = F,
          column.labels = c("Binary for missing"),
          
          keep = c("exposed_at_least_zero","hhm_sex" , "hhm_age", "hh_size" ,  "marital_status_hhm", "literacy_hhm", "education_high","hh_head_religion","hh_ethnic_group", "nbr_female", "nbr_underfive", "nbr_yngchldrn_5_10", "nbr_teenager_10_20", "nbr_adults_20_65", "nbr_female_underfive", "nbr_female_yngchldrn_5_10", "nbr_female_teenager_10_20", "nbr_female_adults_20_65"), notes = "Author's owns computations")

```

#### For children of interest


```{r}
# Table 1
df_global_corrected %>% 
  filter(hh_id %in% lst_menage) %>%
  select(weight_kg,height_cm,hhm_sex,hhm_age,relation_hhh,marital_status_hhm,literacy_hhm,education_high,hh_head_religion,hh_ethnic_group, affected_upazila, waz_who, haz_who, bmiz_who) %>% 
  mutate(affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE),
         hhm_age = as.numeric(hhm_age)) %>%
      # Generate a summary table using "tbl_summary" for the specified columns
    tbl_summary(
    by = affected_upazila, 
     label = list(
       hh_head_religion ~ "Religion",
       hh_ethnic_group  ~ "Ethnc",
       relation_hhh~"Relation with head",
       weight_kg ~ "Weight (kg)",
       height_cm ~ "Height (cm)",
      # affected_upazila ~ "Affected upazila",
       hhm_sex ~ "Sex", 
       hhm_age ~ "Age", 
       marital_status_hhm ~ "Marital status", 
       literacy_hhm ~ "Literacy" , 
       education_high ~ "Education",
       waz_who ~ "WAZ", 
       haz_who ~ "HAZ", 
       bmiz_who ~ "BMIZ"),
    
    type = list(
       hhm_age ~ "continuous" 
      ),
    statistic = list(
      all_categorical() ~ "{n} ({p}%)",
      all_continuous() ~ "{mean} ({sd})"
    ),
    missing_text = "(Missing)",
    digits = list(all_continuous() ~ c(2,2)),
    missing = "ifany"
  ) %>%
       add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) %>% 
  modify_header(label ~ "Affected Upazila") %>% 
  add_overall(last=TRUE)

# Table 2
df_global_corrected %>% 
  filter(hh_id %in% lst_menage) %>%
  select(weight_kg,height_cm,hhm_sex,hhm_age,relation_hhh,marital_status_hhm,literacy_hhm,education_high,hh_head_religion,hh_ethnic_group, high_exposed, waz_who, haz_who, bmiz_who) %>% 
  mutate(high_exposed = factor(high_exposed, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE),
         hhm_age = as.numeric(hhm_age)) %>%
      # Generate a summary table using "tbl_summary" for the specified columns
    tbl_summary(
    by = high_exposed, 
     label = list(
       hh_head_religion ~ "Religion",
       hh_ethnic_group  ~ "Ethnc",
       relation_hhh~"Relation with head",
       weight_kg ~ "Weight (kg)",
       height_cm ~ "Height (cm)",
      # affected_upazila ~ "Affected upazila",
       hhm_sex ~ "Sex", 
       hhm_age ~ "Age", 
       marital_status_hhm ~ "Marital status", 
       literacy_hhm ~ "Literacy" , 
       education_high ~ "Education",
       waz_who ~ "WAZ", 
       haz_who ~ "HAZ", 
       bmiz_who ~ "BMIZ"),
    
    type = list(
       hhm_age ~ "continuous" 
      ),
    statistic = list(
      all_categorical() ~ "{n} ({p}%)",
      all_continuous() ~ "{mean} ({sd})"
    ),
    missing_text = "(Missing)",
    digits = list(all_continuous() ~ c(2,2)),
    missing = "ifany"
  ) %>%
       add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) %>% 
  modify_header(label ~ "Highly Affected Union") %>% 
  add_overall(last=TRUE)


# Table 3
df_global_corrected %>% 
  filter(hh_id %in% lst_menage) %>%
  select(weight_kg,height_cm,hhm_sex,hhm_age,relation_hhh,marital_status_hhm,literacy_hhm,education_high,hh_head_religion,hh_ethnic_group, exposed_at_least_zero, waz_who, haz_who, bmiz_who) %>% 
  mutate(exposed_at_least_zero = factor(exposed_at_least_zero, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE),
         hhm_age = as.numeric(hhm_age)) %>%
      # Generate a summary table using "tbl_summary" for the specified columns
    tbl_summary(
    by = exposed_at_least_zero, 
     label = list(
       hh_head_religion ~ "Religion",
       hh_ethnic_group  ~ "Ethnc",
       relation_hhh~"Relation with head",
       weight_kg ~ "Weight (kg)",
       height_cm ~ "Height (cm)",
      # affected_upazila ~ "Affected upazila",
       hhm_sex ~ "Sex", 
       hhm_age ~ "Age", 
       marital_status_hhm ~ "Marital status", 
       literacy_hhm ~ "Literacy" , 
       education_high ~ "Education",
       waz_who ~ "WAZ", 
       haz_who ~ "HAZ", 
       bmiz_who ~ "BMIZ"),
    
    type = list(
       hhm_age ~ "continuous" 
      ),
    statistic = list(
      all_categorical() ~ "{n} ({p}%)",
      all_continuous() ~ "{mean} ({sd})"
    ),
    missing_text = "(Missing)",
    digits = list(all_continuous() ~ c(2,2)),
    missing = "ifany"
  ) %>%
       add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) %>% 
  modify_header(label ~ "Affected Union") %>% 
  add_overall(last=TRUE)
```


In the following, I restrict the sample to the households members that are of interest (under 20 years of age). I then 

```{r}


all_comb <- df_global_corrected %>%
            select(hh_id, member_id, survey_year) %>% 
            filter(hh_id %in% lst_menage) %>% 
            tidyr::expand(member_id,survey_year)

# Use with `right_join()` to fill in missing rows (in data)
all_comb <- df_global_corrected %>%
            select(hh_id, member_id, survey_year, affected_upazila, treat_group, weight_kg, hhm_age, if_not_measured_why, haz_who, bmiz_who) %>% 
            filter(hh_id %in% lst_menage) %>% 
  dplyr::right_join(all_comb, by=c("member_id","survey_year")) %>% 
  mutate(treat_group = ifelse((survey_year < 2018) & (is.na(treat_group)),0, treat_group))

lst_treat_people <- all_comb %>% filter(treat_group==1) %>% select(member_id) %>% distinct() %>% pull()

all_comb <- all_comb %>% 
  mutate(treat_group = ifelse((survey_year == 2018) & (is.na(treat_group)) & (member_id %in% lst_treat_people),1, ifelse( (survey_year == 2018) & (is.na(treat_group)) & !(member_id %in% lst_treat_people),0, treat_group)))

panelView::panelview(haz_who ~ treat_group + weight_kg + hhm_age, gridOff = TRUE, by.timing = TRUE, data = all_comb, index = c("member_id","survey_year"), 
          type = "outcome", main = "", 
          ylim = c(-5,5),xlab = "Year", ylab = "Nbr individuals")
```
```{r}
panelView::panelview(haz_who ~ treat_group + weight_kg + hhm_age, gridOff = TRUE, by.timing = TRUE, data = all_comb, index = c("member_id","survey_year"), 
          type = "outcome", by.group = TRUE, cex.main = 20, cex.main.sub = 15,xlab = "Year", ylab = "Nbr individuals")
```


```{r, results='hold', include = TRUE, warning=FALSE, echo = FALSE}


panelView::panelview(1 ~ treat_group + weight_kg, gridOff = TRUE, by.timing = TRUE, data = all_comb, index = c("member_id","survey_year"), display.all = TRUE,
          xlab = "Year", ylab = "Nbr individuals", pre.post = TRUE, by.unit=TRUE,  background = "white",cex.main = 20, cex.axis= 8, cex.lab = 12, cex.legend = 12, collapse.history = "TRUE", main = "")
```
Missing data in the outcome variables (or components of them) at the individual level can come from several sources. Affected individuals are more likely to provide missing information because of:

* Absence (88% vs 86%) and refusal to answer (4.7% vs 2.2%)

```{r}
df_global %>% 
  filter(hh_id %in% lst_menage) %>%
  filter(if_not_measured_why!="have measured") %>% 
  select(if_not_measured_why, affected_upazila) %>% 
  mutate(affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE)) %>%
      # Generate a summary table using "tbl_summary" for the specified columns
    tbl_summary(
    by = affected_upazila, 
     label = list(
       if_not_measured_why  ~ "Reason for being missing in outcome"),
    
    #type = list(
       #hhm_age ~ "continuous" 
      #),
    statistic = list(
      all_categorical() ~ "{n} ({p}%)",
      all_continuous() ~ "{mean} ({sd})"
    ),
    missing_text = "(Missing)",
    digits = list(all_continuous() ~ c(2,2)),
    missing = "ifany"
  ) %>%
       add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) %>% 
  modify_header(label ~ "") %>% 
  add_overall(last=TRUE)
```
This table presents a regression analysis to identify factors that may explain why some individuals have NaN values in their outcome variables. It shows that the probability of being missing increases with:

* Being in a cyclone-affected upazila (possibly due to sickness)
* Being male (probably because they are more likely to be absent)
* Age
* Household size (the larger the household, the more likely there is an individual with missing)
* Literacy and having a diploma are negatively correlated with the probability of being missing



```{r, results='hold', include = TRUE, warning=FALSE, echo = FALSE}
df_reg <- df_global %>% 
  filter(hh_id %in% lst_menage) %>%
  # Selecting relevant variables
  mutate(out_missing = ifelse(if_not_measured_why=="have measured",0,1)) %>% 
  mutate(time_bin = as.factor(ifelse(survey_year>=2018,1,0)),
         affected_upazila = as.factor(affected_upazila))

#stargazer(regsplit,  type = "text", title = "Split and household characteristics")

regnan_1 <- felm(out_missing ~ affected_upazila*time_bin, data=df_reg)

regnan_2 <- felm(out_missing ~ affected_upazila*time_bin + hhm_sex + hhm_age +  marital_status_hhm + hh_size + literacy_hhm + education_high +  hh_head_religion + hh_ethnic_group + relation_hhh + affected_upazila + nbr_female+ nbr_underfive+ nbr_yngchldrn_5_10 + nbr_teenager_10_20+ nbr_adults_20_65+ nbr_female_underfive+ nbr_female_yngchldrn_5_10 + nbr_female_teenager_10_20 + nbr_female_adults_20_65, data=df_reg)

regnan_3 <- felm(out_missing ~ affected_upazila*time_bin + hhm_sex + hhm_age + marital_status_hhm + hh_size + literacy_hhm + education_high +  hh_head_religion + hh_ethnic_group + relation_hhh + affected_upazila + nbr_female+ nbr_underfive+ nbr_yngchldrn_5_10 + nbr_teenager_10_20+ nbr_adults_20_65+ nbr_female_underfive+ nbr_female_yngchldrn_5_10 + nbr_female_teenager_10_20 + nbr_female_adults_20_65|0|0|affected_upazila, data=df_reg)



stargazer(regnan_1, regnan_2,regnan_3, type = "text", title = "Prob. of missing", digits=2, float = TRUE,se.position = "below", omit.stat=c("LL","ser","f","adj.rsq","res.dev"), dep.var.labels.include = TRUE,font.size="small",
          se.position = "below",notes.align = "l",table.placement = "H",header = F,
          column.labels = c("Binary for missing"),
          
          keep = c("affected_upazila","time_bin","affected_upazila:time_bin","hhm_sex" , "hhm_age", "hh_size" ,  "marital_status_hhm", "literacy_hhm", "education_high","hh_head_religion","hh_ethnic_group", "affected_upazila","nbr_female", "nbr_underfive", "nbr_yngchldrn_5_10", "nbr_teenager_10_20", "nbr_adults_20_65", "nbr_female_underfive", "nbr_female_yngchldrn_5_10", "nbr_female_teenager_10_20", "nbr_female_adults_20_65"), notes = "Author's owns computations")


```


Affected household seems to have more new member than non affected household.


```{r}
df_global %>% 
  filter(hh_id %in% lst_menage) %>%
  select(hhm_status, affected_upazila) %>% 
  mutate(affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE)) %>%
      # Generate a summary table using "tbl_summary" for the specified columns
    tbl_summary(
    by = affected_upazila, 
     label = list(
       hhm_status  ~ "Member status"),
    
    #type = list(
       #hhm_age ~ "continuous" 
      #),
    statistic = list(
      all_categorical() ~ "{n} ({p}%)",
      all_continuous() ~ "{mean} ({sd})"
    ),
    missing_text = "(Missing)",
    digits = list(all_continuous() ~ c(2,2)),
    missing = "ifany"
  ) %>%
       add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) %>% 
  modify_header(label ~ "") %>% 
  add_overall(last=TRUE)
```



The following table summarizes each household member's history during the second and third survey rounds, depending on their status during the first survey round:

* Among the members in the first round:
  - N = 19298 (77.6 percent) were permanent household members during the first round;
  - N = 3094 (12.4 percent) individuals joined the household later for reasons not related to birth;
    - N = 2473 (10 percent) children were unborn during the first round but joined the household later (during r2 or r3);
  - N = 3 (<1 percent) are unsure or missing.




```{r, results='hold', include = TRUE, warning=FALSE, echo = FALSE}

# niveau individus
lst_menage <- df_r1_hh %>% 
  mutate(hh_split_r2_r3 = ifelse(hh_split_r3=="1"| hh_split_r2=="1","1","0"),
         attrition = ifelse(interview_status_r3=="Complete","0","1")) %>% 
  filter(hh_split_r2_r3=="0") %>%  
  filter(attrition=="0") %>% 
  dplyr::select(hh_id) %>% 
  pull()

lst_later_join = c('New member through marriage','New member upon return from divorce or seperation','Household merged/combined','Other reasons (permanent)','Residing elsewhere for the pursuit of studies')

#'Death','Married and left household','Divorced and left household','Household split','Left household for employment','Other reasns for leaving the household','New sample household and current round member'

tbl_data <- df_r2_anthr1 %>% 
  filter(hh_id %in% lst_menage) %>% 
  select(member_id, hhm_status) %>% 
  rename(hhm_status_r2 = hhm_status) %>%
  plyr::rbind.fill(
    df_r2_anthr2 %>% 
      filter(hh_id %in% lst_menage) %>% 
      select(member_id, hhm_status) %>% 
      rename(hhm_status_r2 = hhm_status)) %>% 
  dplyr::full_join(
    df_r3_anthr1 %>% 
      filter(hh_id %in% lst_menage) %>% 
      select(member_id, hhm_status) %>% 
      rename(hhm_status_r3 = hhm_status) %>%
    plyr::rbind.fill(
      df_r3_anthr2 %>% 
        filter(hh_id %in% lst_menage) %>% 
        select(member_id, hhm_status) %>% 
        rename(hhm_status_r3 = hhm_status))) %>% 
  dplyr::full_join(
    df_r1_anthr1 %>% 
      filter(hh_id %in% lst_menage) %>% 
      select(member_id, hhm_status) %>% 
      rename(hhm_status_r1 = hhm_status) %>%
    plyr::rbind.fill(
      df_r1_anthr2 %>% 
        filter(hh_id %in% lst_menage) %>% 
        select(member_id, hhm_status) %>% 
        rename(hhm_status_r1 = hhm_status))) %>% 
  select(member_id, hhm_status_r1, hhm_status_r2, hhm_status_r3) %>% 
  mutate(hhm_status_r2 = ifelse(is.na(hhm_status_r1) & is.na(hhm_status_r2) & (hhm_status_r3 == "New member (new born)"),"Unborn", ifelse(is.na(hhm_status_r1) & is.na(hhm_status_r2) & (hhm_status_r3 %in% lst_later_join),"Join later",hhm_status_r2)),
         
hhm_status_r1 = ifelse(is.na(hhm_status_r1) & (hhm_status_r2 == "New member (new born)"),"Unborn",ifelse(is.na(hhm_status_r1) & (hhm_status_r2 %in% c(lst_later_join, "Join later")),"Join later",ifelse(is.na(hhm_status_r1) & (hhm_status_r2 == "Unborn"),"Unborn",  hhm_status_r1))))

tbl_data <- tbl_data %>% 
  mutate(hhm_status_r1 = replace_na(hhm_status_r1, "Missing"),
         hhm_status_r2 = replace_na(hhm_status_r2, "Missing"),
         hhm_status_r3 = replace_na(hhm_status_r3, "Missing"))

tbl_data %>% 
  select(hhm_status_r1, hhm_status_r2, hhm_status_r3) %>% 
  tbl_strata(
    strata = hhm_status_r1,
    .tbl_fun =
      ~ .x %>%
      tbl_summary(
    by = hhm_status_r3, 
      label = list(
        hhm_status_r3 ~ "Status R3",
        hhm_status_r2 ~ "Status R2"
     ),
    statistic = list(
      all_categorical() ~ "{n} ({p}%)",
      all_continuous() ~ "{mean} ({sd})"
    ),
    missing_text = "(Missing)",
    digits = everything() ~ c(0,2),
    missing = "ifany"
  ) %>%
      add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) %>%
      # Modify the table header to provide a descriptive label
      modify_header(label ~ "Member status in R2 vs R3"),
    # Add difference statistics to the table
    #add_difference(),
    .header = "**{strata}**, N = {n}",
    #.combine_with = "tbl_stack",
    #.combine_args = list(group_header = NULL),
    .quiet = TRUE) 
```

There is 578 individuals with always NaN values for the three survey round. Among these we have people that are always sick or absent or even born during the last round but with NaN values in it.


```{r results='hold', include = TRUE, warning=FALSE, echo = FALSE}

# niveau individus
lst_menage <- df_r1_hh %>% 
  mutate(hh_split_r2_r3 = ifelse(hh_split_r3=="1"| hh_split_r2=="1","1","0"),
         attrition = ifelse(interview_status_r3=="Complete","0","1")) %>% 
  filter(hh_split_r2_r3=="0") %>%  
  filter(attrition=="0") %>% 
  dplyr::select(hh_id) %>% 
  pull()

all_comb <- df_global %>%
            select(hh_id, member_id, survey_year) %>% 
            filter(hh_id %in% lst_menage) %>% 
            tidyr::expand(member_id,survey_year)

# Use with `right_join()` to fill in missing rows (in data)
all_comb <- df_global %>%
            select(hh_id, member_id, survey_year, affected_upazila, treat_group, weight_kg, hhm_age, if_not_measured_why) %>% 
            filter(hh_id %in% lst_menage) %>% 
  dplyr::right_join(all_comb, by=c("member_id","survey_year")) %>% 
  mutate(treat_group = ifelse((survey_year < 2018) & (is.na(treat_group)),0, treat_group))

lst_treat_people <- all_comb %>% filter(treat_group==1) %>% select(member_id) %>% distinct() %>% pull()

all_comb <- all_comb %>% 
  mutate(treat_group = ifelse((survey_year == 2018) & (is.na(treat_group)) & (member_id %in% lst_treat_people),1, ifelse( (survey_year == 2018) & (is.na(treat_group)) & !(member_id %in% lst_treat_people),0, treat_group)))

panelView::panelview(1 ~ treat_group + weight_kg, gridOff = TRUE, by.timing = TRUE, data = all_comb, index = c("member_id","survey_year"), display.all = TRUE,
          xlab = "Year", ylab = "Nbr individuals", pre.post = TRUE, by.unit=TRUE,  background = "white",cex.main = 20, cex.axis= 8, cex.lab = 12, cex.legend = 12, collapse.history = "TRUE", main = "")

```

Now, I would like to understand the factors that can explain the probability of being missing after the disaster (the attrition at the individual level). I ran a regression after the disaster to understand the characteristics that can explain the probability of being missing. I found that the same factors from the previous analysis explain the probability of being missing.




```{r, results='hold', include = TRUE, warning=FALSE, echo = FALSE}
df_reg <- df_global %>% 
  filter(hh_id %in% lst_menage) %>%
  filter(survey_round==3) %>% 
  # Selecting relevant variables
  mutate(out_missing = ifelse(if_not_measured_why=="have measured",0,1)) %>% 
  mutate(time_bin = as.factor(ifelse(survey_year>=2018,1,0)),
         affected_upazila = as.factor(affected_upazila))

#stargazer(regsplit,  type = "text", title = "Split and household characteristics")

regnan_1 <- felm(out_missing ~ affected_upazila, data=df_reg)

regnan_2 <- felm(out_missing ~ affected_upazila + hhm_sex + hhm_age +  marital_status_hhm + hh_size + literacy_hhm + education_high +  hh_head_religion + hh_ethnic_group + relation_hhh + affected_upazila + nbr_female+ nbr_underfive+ nbr_yngchldrn_5_10 + nbr_teenager_10_20+ nbr_adults_20_65+ nbr_female_underfive+ nbr_female_yngchldrn_5_10 + nbr_female_teenager_10_20 + nbr_female_adults_20_65, data=df_reg)

regnan_3 <- felm(out_missing ~ affected_upazila + hhm_sex + hhm_age + marital_status_hhm + hh_size + literacy_hhm + education_high +  hh_head_religion + hh_ethnic_group + relation_hhh + affected_upazila + nbr_female+ nbr_underfive+ nbr_yngchldrn_5_10 + nbr_teenager_10_20+ nbr_adults_20_65+ nbr_female_underfive+ nbr_female_yngchldrn_5_10 + nbr_female_teenager_10_20 + nbr_female_adults_20_65|0|0|affected_upazila, data=df_reg)



stargazer(regnan_1, regnan_2,regnan_3, type = "text", title = "Prob. of missing", digits=2, float = TRUE,se.position = "below", omit.stat=c("LL","ser","f","adj.rsq","res.dev"), dep.var.labels.include = TRUE,font.size="small",
          se.position = "below",notes.align = "l",table.placement = "H",header = F,
          column.labels = c("Binary for missing"),
          
          keep = c("affected_upazila","hhm_sex" , "hhm_age", "hh_size" ,  "marital_status_hhm", "literacy_hhm", "education_high","hh_head_religion","hh_ethnic_group", "affected_upazila","nbr_female", "nbr_underfive", "nbr_yngchldrn_5_10", "nbr_teenager_10_20", "nbr_adults_20_65", "nbr_female_underfive", "nbr_female_yngchldrn_5_10", "nbr_female_teenager_10_20", "nbr_female_adults_20_65"), notes = "Author's owns computations")



```

### Analysis of the evolution of the weight et height before and after disaster


```{r}

df_reg <- df_global %>%
  select(hh_id, member_id, survey_year, affected_upazila, treat_group, weight_kg, hhm_age,height_cm, if_not_measured_why) %>% 
  filter(hh_id %in% lst_menage) 
  

panelView::panelview(weight_kg ~ treat_group + height_cm, 
          data = df_reg, index = c("member_id","survey_year"), 
          type = "outcome", main = "", pre.post = TRUE)

panelView::panelview(height_cm ~ treat_group + weight_kg, 
          data = df_reg, index = c("member_id","survey_year"), 
          type = "bivariate", main = "", pre.post = TRUE,
          style = c("c","l"))
```


```{r eval=FALSE, warning=FALSE, include=FALSE, results='hide'}
# niveau individus

lst_menage = df_r1_hh %>% 
      filter(hh_split_r2==0 & hh_split_r3==0 & interview_status_r3=="Complete") %>% 
      select(hh_id) %>% 
      pull()

lst_ind <- df_r3_anthr2 %>% 
            select(hh_id,member_id, hhm_status, hhm_age) %>%
            filter(hh_id %in% lst_menage & hhm_status=="Both previous round and current round member" & hhm_age >= 3) %>% 
            plyr::rbind.fill(df_r3_anthr1 %>% 
            select(hh_id,member_id, hhm_status, hhm_age) %>% 
            filter(hh_id %in% lst_menage & hhm_status=="Both previous round and current round member" & hhm_age < 20)) %>% 
            # filter(hh_id %in% lst_menage) %>% 
            # filter(hhm_status=="Both previous round and current round member") %>% 
            # filter(hhm_age >= 3 & hhm_age < 20) %>% 
            select(member_id) %>% 
            pull()

all_comb <- df_global %>%
            dplyr::select(member_id, survey_year) %>% 
            dplyr::filter(member_id %in% lst_ind) %>% 
            expand(member_id,survey_year)

# Use with `right_join()` to fill in missing rows (in data)
all_comb <- df_global %>%
            select(hh_id,hhm_id, member_id, survey_year, affected_upazila, treat_group, height_cm, weight_kg) %>% 
            filter(hh_id %in% lst_menage) %>% 
  dplyr::right_join(all_comb) 

panelView::panelview(1 ~ treat_group + weight_kg, gridOff = TRUE, by.timing = TRUE,
          data = all_comb, index = c("member_id","survey_year"), display.all = TRUE,
          xlab = "Year", ylab = "Nbr individuals", pre.post = TRUE, by.unit=TRUE,  background = "white",cex.main = 20, cex.axis= 8, cex.lab = 12, cex.legend = 12, shade.post = TRUE, collapse.history = "TRUE", main = "Traitement status")
```



```{r eval=FALSE, warning=FALSE, include=FALSE, results='hide'}

df_r2_hh %>% 
  distinct(hh_id_parent, .keep_all = TRUE) %>% 
  # Selecting relevant variables
  # , labels = c("No affected district", "Affected district"),
   select(hh_split, affected_upazila) %>% 
  mutate(sample='round 2',      
         hh_split = factor(hh_split, levels = c("0", "1"),labels = c("No", "Yes"),ordered = TRUE), affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE)) %>% 
  
  plyr::rbind.fill(
    #For the sibling dataset
    df_r3_hh %>%
      distinct(hh_id_parent, .keep_all = TRUE) %>% 
  # Selecting relevant variables
   select(hh_split, affected_upazila) %>% 
  #rename(affected_upazila=Affected_district) %>% 
   mutate( 
     sample='round 3',
     hh_split = factor(hh_split, levels = c("0", "1"), labels = c("No", "Yes"), ordered = TRUE), affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE))) %>%
    tbl_strata(
    strata = sample,
    .tbl_fun =
      ~ .x %>%
      # Generate a summary table using "tbl_summary" for the specified columns
      tbl_summary(
    by = affected_upazila, 
      label = list(
        hh_split ~ "Household split (1=Yes, 0=No)"
    #    height_cm ~ "height (cm)",
    #    hhm_sex ~ "Sex",
    #    hhm_age ~ "age (in year)",
    #    relation_hhh ~ "relation with the head",
    #    if_not_measured_why ~ "Why missing"
    #    
     ),
    statistic = list(
      all_categorical() ~ "{n} ({p}%)",
      all_continuous() ~ "{mean} ({sd})"
    ),
    missing_text = "(Missing)",
    digits = everything() ~ c(0,2),
    missing = "always"
  ) %>%
      add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) %>%
      # Modify the table header to provide a descriptive label
      modify_header(label ~ ""),
    # Add difference statistics to the table
    #add_difference(),
    .header = "**{strata}**, N = {n}") #%>%
  #as_gt() %>%
  #gt::gtsave('desc_table_summary.tex', path = here::here())
```


```{r eval=FALSE, warning=FALSE, include=FALSE, results='hide'}

# df_r2_hh %>% 
#   #distinct(hh_id_parent, .keep_all = TRUE) %>% 
#   # Selecting relevant variables
#   # , labels = c("No affected district", "Affected district"),
#    select(hh_split_bis, affected_upazila) %>% 
#   mutate(sample='round 2',      
#          hh_split_bis = factor(hh_split_bis, levels = c("0", "1"),labels = c("No", "Yes"),ordered = TRUE), affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE)) %>% 
#   
#   plyr::rbind.fill(
#     #For the sibling dataset
#     df_r3_hh %>%
#       #distinct(hh_id_parent, .keep_all = TRUE) %>% 
#   # Selecting relevant variables
#    select(hh_split_bis, affected_upazila) %>% 
#   #rename(affected_upazila=Affected_district) %>% 
#    mutate( 
#      sample='round 3',
#      hh_split_bis = factor(hh_split_bis, levels = c("0", "1"), labels = c("No", "Yes"), ordered = TRUE), affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE))) %>%
#     tbl_strata(
#     strata = sample,
#     .tbl_fun =
#       ~ .x %>%
#       # Generate a summary table using "tbl_summary" for the specified columns
#       tbl_summary(
#     by = affected_upazila, 
#       label = list(
#         hh_split_bis ~ "Household split infant (1=Yes, 0=No)"
#     #    height_cm ~ "height (cm)",
#     #    hhm_sex ~ "Sex",
#     #    hhm_age ~ "age (in year)",
#     #    relation_hhh ~ "relation with the head",
#     #    if_not_measured_why ~ "Why missing"
#     #    
#      ),
#     statistic = list(
#       all_categorical() ~ "{n} ({p}%)",
#       all_continuous() ~ "{mean} ({sd})"
#     ),
#     missing_text = "(Missing)",
#     digits = everything() ~ c(0,2),
#     missing = "always"
#   ) %>%
#       add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) %>%
#       # Modify the table header to provide a descriptive label
#       modify_header(label ~ ""),
#     # Add difference statistics to the table
#     #add_difference(),
#     .header = "**{strata}**, N = {n}") #%>%
#   #as_gt() %>%
#   #gt::gtsave('desc_table_summary.tex', path = here::here())
```



### Interview status

Theses tables summarize the interview status for hh survey in round 2 (before the TC Mora) and in round 3 (after the TC Mora).

4690 hhs in round 3 have completed informations, I will take these to see how it affected. I should have at most 4690 household in R1 and R2 
```{r eval=FALSE, warning=FALSE, include=FALSE, results='hide'}


df_r1_hh %>% 

  # if you don't remove those who split between R1 and R2 you don't take into account the hh that split and disapear during R3.
  filter(hh_split_r2==0 & hh_split_r3==0) %>% 
  # Selecting relevant variables
   select(interview_status_r2,interview_status_r3) %>% 
  

      # Generate a summary table using "tbl_summary" for the specified columns
    tbl_summary(
    by = interview_status_r3, 
     label = list(
       interview_status_r2 ~ "Status R2",
       interview_status_r3 ~ "Status R3"),
    
    statistic = list(
      all_categorical() ~ "{n} ({p}%)",
      all_continuous() ~ "{mean} ({sd})"
    ),
    
    missing_text = "(Missing)",
    digits = everything() ~ c(0,2),
    missing = "ifany"
  ) %>%
       add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) %>% 
  modify_header(label ~ "**Status R3**") 
```



```{r eval=FALSE, warning=FALSE, include=FALSE, results='hide'}
df_r1_hh %>% 

  # Selecting relevant variables
   select(interview_status_r2,interview_status_r3,affected_upazila) %>% 
     mutate(
       affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE)) %>% 
    tbl_strata(
    strata = affected_upazila,
    .tbl_fun =
      ~ .x %>%
      # Generate a summary table using "tbl_summary" for the specified columns
    tbl_summary(
    by = interview_status_r3, 
     label = list(
       interview_status_r2 ~ "Status R2",
       interview_status_r3 ~ "Status R3"),
    statistic = list(
      all_categorical() ~ "{n} ({p}%)",
      all_continuous() ~ "{mean} ({sd})"
    ),
    missing_text = "(Missing)",
    digits = everything() ~ c(0,2),
    missing = "ifany"
  ) %>%
       add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) %>% 
      # Modify the table header to provide a descriptive label
      modify_header(label ~ ""),
    # Add difference statistics to the table
    #add_difference(),
    .header = "**{strata}**, N = {n}") #%>%
```


Here is 4603 (98.14 percent) hh for which information on the R2 is available. The remaining 87 didn't complete the information on R2 but complete the information on R1. The 65 remaining hh migrated in r2 but complete the survey in r3 (very strange). They were able to identify in r3 were the hh migrated too (where it go). I keep them in the data.

R3 = 4690
R2 = 4603-(87) = 4603
R1 = 4690
```{r eval=FALSE, warning=FALSE, include=FALSE, results='hide'}

df_r1_hh %>% 

  # if you don't remove those who split between R1 and R2 you don't take into account the hh that split and disapear during R3.
  filter(hh_split_r2==0 & hh_split_r3==0 & interview_status_r3=="Complete") %>% 

mutate(affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE)) %>%
  # Selecting relevant variables
   select(interview_status_r2,affected_upazila, hh_size) %>% 
  

      # Generate a summary table using "tbl_summary" for the specified columns
    tbl_summary(
    by = interview_status_r2, 
     label = list(
       affected_upazila ~ "Affected_upazila",
       hh_size ~ "hh size"
       ),
    
    statistic = list(
      all_categorical() ~ "{n} ({p}%)",
      all_continuous() ~ "{mean} ({sd})"
    ),
    
    missing_text = "(Missing)",
    digits = list(hh_size ~ c(2, 2)),
    missing = "ifany"
  ) %>%
       add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) %>% 
  modify_header(label ~ "**Status R3**") 

```




### Hh's head religion

```{r eval=FALSE, warning=FALSE, include=FALSE, results='hide'}

df_r1_hh %>% 
   select(hh_head_religion, affected_upazila) %>% 
  mutate(sample='round 1',      
         hh_head_religion = factor(hh_head_religion), 
         affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE)) %>%
  
  plyr::rbind.fill(df_r2_hh %>% 
   select(hh_head_religion, affected_upazila) %>% 
  mutate(sample='round 2',      
         hh_head_religion = factor(hh_head_religion), affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE))) %>% 
  
  plyr::rbind.fill(
    df_r3_hh %>%
  # Selecting relevant variables
   select(hh_head_religion, affected_upazila) %>% 
   mutate( 
     sample='round 3',
     hh_head_religion = factor(hh_head_religion), 
     affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE))) %>%
    tbl_strata(
    strata = sample,
    .tbl_fun =
      ~ .x %>%
      # Generate a summary table using "tbl_summary" for the specified columns
      tbl_summary(
    by = affected_upazila, 
      label = list(
        hh_head_religion ~ "hh head religion"
     ),
    statistic = list(
      all_categorical() ~ "{n} ({p}%)",
      all_continuous() ~ "{mean} ({sd})"
    ),
    missing_text = "(Missing)",
    digits = everything() ~ c(0,2),
    missing = "always"
  ) %>%
      add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) %>%
      # Modify the table header to provide a descriptive label
      modify_header(label ~ ""),
    .header = "**{strata}**, N = {n}") 
```

```{r eval=FALSE, warning=FALSE, include=FALSE, results='hide'}
df_r1_hh %>% 
  #distinct(hh_id_parent, .keep_all = TRUE) %>% 
  # Selecting relevant variables
  # , labels = c("No affected district", "Affected district"),
   select(hh_head_religion, interview_status_r2, interview_status_r3) %>% 
  mutate(
         #interview_status = factor(interview_status),
         interview_status_r2 = factor(interview_status_r2), 
         interview_status_r3 = factor(interview_status_r3)) %>% 
  
      # Generate a summary table using "tbl_summary" for the specified columns
  tbl_summary(
  by = hh_head_religion, 
      label = list(
        hh_head_religion ~ "hh head religion",
        #interview_status ~ "interview status round 1",
        interview_status_r2 ~ "interview status round 2",
        interview_status_r3 ~ "interview status round 3"
    #    hhm_age ~ "age (in year)",
    #    relation_hhh ~ "relation with the head",
    #    if_not_measured_why ~ "Why missing"
    #    
     ),
    statistic = list(
      all_categorical() ~ "{n} ({p}%)",
      all_continuous() ~ "{mean} ({sd})"
    ),
    missing_text = "(Missing)",
    digits = everything() ~ c(0,2),
    missing = "always"
  ) %>%
      add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) 
  #as_gt() %>%
  #gt::gtsave('desc_table_summary.tex', path = here::here())
```


### Hh head ethnicity

```{r eval=FALSE, warning=FALSE, include=FALSE, results='hide'}

df_r1_hh %>% 
   select(hh_ethnic_group, affected_upazila) %>% 
  mutate(sample='round 1',      
         hh_ethnic_group = factor(hh_ethnic_group), 
         affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE)) %>%
  
  plyr::rbind.fill(df_r2_hh %>% 
   select(hh_ethnic_group, affected_upazila) %>% 
  mutate(sample='round 2',      
         hh_ethnic_group = factor(hh_ethnic_group), affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE))) %>% 
  
  plyr::rbind.fill(
    df_r3_hh %>%
  # Selecting relevant variables
   select(hh_ethnic_group, affected_upazila) %>% 
   mutate( 
     sample='round 3',
     hh_ethnic_group = factor(hh_ethnic_group), 
     affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE))) %>%
    tbl_strata(
    strata = sample,
    .tbl_fun =
      ~ .x %>%
      # Generate a summary table using "tbl_summary" for the specified columns
      tbl_summary(
    by = affected_upazila, 
      label = list(
        hh_ethnic_group ~ "hh head ethnic group"
     ),
    statistic = list(
      all_categorical() ~ "{n} ({p}%)",
      all_continuous() ~ "{mean} ({sd})"
    ),
    missing_text = "(Missing)",
    digits = everything() ~ c(0,2),
    missing = "always"
  ) %>%
      add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) %>%
      # Modify the table header to provide a descriptive label
      modify_header(label ~ ""),
    .header = "**{strata}**, N = {n}") 
```

```{r eval=FALSE, warning=FALSE, include=FALSE, results='hide'}
# 
# df_r1_hh %>% 
# 
#   # Selecting relevant variables
#    select(weight_kg,height_cm,if_not_measured_why,hhm_sex,hhm_age,relation_hhh,affected_upazila) %>% 
#   mutate(sample='round 1') %>% 
#   
#   plyr::rbind.fill(
#     #For the sibling dataset
#     r2_data %>%
# select(weight_kg,height_cm,if_not_measured_why,hhm_sex,hhm_age,relation_hhh, affected_upazila) %>% 
#   #rename(affected_upazila=Affected_district) %>% 
#    mutate( 
#      sample='round 2',
#      affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected district", "Affected district"), ordered = TRUE)) %>% 
#   filter(!is.na(if_not_measured_why))) %>%
# 
#   tbl_strata(
#     strata = sample,
#     .tbl_fun =
#       ~ .x %>%
#       # Generate a summary table using "tbl_summary" for the specified columns
#       tbl_summary(
#     by = affected_upazila, 
#      label = list(
#        weight_kg ~ "weight (kg)",
#        height_cm ~ "height (cm)",
#        hhm_sex ~ "Sex",
#        hhm_age ~ "age (in year)",
#        relation_hhh ~ "relation with the head",
#        if_not_measured_why ~ "Why missing"
#        
#     ),
#     statistic = list(
#       all_categorical() ~ "{n} ({p}%)",
#       all_continuous() ~ "{mean} ({sd})"
#     ),
#     missing_text = "(Missing)",
#     digits = everything() ~ c(2,2),
#     missing = "always"
#   ) %>%
#       add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) %>%
#       # Modify the table header to provide a descriptive label
#       modify_header(label ~ "Characteristics of children"),
#     # Add difference statistics to the table
#     #add_difference(),
#     .header = "**{strata}**, N = {n}") #%>%
#   #as_gt() %>%
#   #gt::gtsave('desc_table_summary.tex', path = here::here())
```

```{r eval=FALSE, warning=FALSE, include=FALSE, results='hide'}

lst_menage = df_r1_hh %>% 
      filter(hh_split_r2==0 & hh_split_r3==0) %>% 
      select(hh_id) %>% 
      pull()

all_comb <- df_r1_hh %>%
            select(hh_id,survey_round) %>% 
            filter(hh_id %in% lst_menage) %>% 
            plyr::rbind.fill(df_r2_hh %>%
            select(hh_id,survey_round)%>% 
            filter(hh_id %in% lst_menage)) %>% 
            plyr::rbind.fill(df_r3_hh %>%
            select(hh_id,survey_round)%>% 
            filter(hh_id %in% lst_menage)) %>% 
            expand(hh_id,survey_round)

# Use with `right_join()` to fill in missing rows (in data)
all_comb <- df_r1_hh %>%
          select(hh_id,survey_round, hh_size, affected_upazila,treat_group, survey_year) %>% 
          filter(hh_id %in% lst_menage)%>% 
          plyr::rbind.fill(df_r2_hh %>%
          select(hh_id,survey_round, hh_size, affected_upazila,treat_group, survey_year)%>% 
          filter(hh_id %in% lst_menage))%>% 
          plyr::rbind.fill(df_r3_hh %>%
          select(hh_id,survey_round, hh_size, affected_upazila,treat_group, survey_year)%>% 
          filter(hh_id %in% lst_menage))%>% 
  dplyr::right_join(all_comb) %>% 
  mutate(
         affected_upazila = ifelse(is.na(hh_size), NA, affected_upazila),
         treat_group = ifelse(is.na(hh_size), NA, treat_group))
# survey_year = ifelse(survey_round==1,2011,
#                               ifelse(survey_round==2,2015,
#                                      ifelse(survey_round==3,2018,NA))),

panelView::panelview( 1 ~ treat_group, gridOff = TRUE, by.timing = TRUE,
          data = all_comb, index = c("hh_id","survey_year"), display.all = TRUE,
          xlab = "Nbr household", ylab = "", pre.post = TRUE, by.unit=TRUE,  background = "white",cex.main = 20, cex.axis= 8, cex.lab = 12, cex.legend = 12, collapse.history = "TRUE", main = "Traitement status")
```


```{r eval=FALSE, warning=FALSE, include=FALSE, results='hide'}
# df_global %>% 
#   mutate(survey_round=as.numeric(survey_round)) %>% 
#   filter(hh_split==0)
#   group_by(member_id) %>% 
#   summarise(n=n(), matot= sum(survey_round)) 

# used expand to create 
# Na because unborn vs NA
# niveau mnage

lst_menage = df_r1_hh %>% 
      filter(hh_split_r2==0 & hh_split_r3==0 & interview_status_r3=="Complete") %>% 
      select(hh_id) %>% 
      pull()

all_comb <- df_r1_hh %>%
            select(hh_id,survey_round) %>% 
            filter(hh_id %in% lst_menage) %>% 
            plyr::rbind.fill(df_r2_hh %>%
            select(hh_id,survey_round)%>% 
            filter(hh_id %in% lst_menage)) %>% 
            plyr::rbind.fill(df_r3_hh %>%
            select(hh_id,survey_round)%>% 
            filter(hh_id %in% lst_menage)) %>% 
            expand(hh_id,survey_round)

# Use with `right_join()` to fill in missing rows (in data)
all_comb <- df_r1_hh %>%
          select(hh_id,survey_round, hh_size, affected_upazila,treat_group, survey_year) %>% 
          filter(hh_id %in% lst_menage)%>% 
          plyr::rbind.fill(df_r2_hh %>%
          select(hh_id,survey_round, hh_size, affected_upazila,treat_group, survey_year)%>% 
          filter(hh_id %in% lst_menage))%>% 
          plyr::rbind.fill(df_r3_hh %>%
          select(hh_id,survey_round, hh_size, affected_upazila,treat_group, survey_year)%>% 
          filter(hh_id %in% lst_menage))%>% 
  dplyr::right_join(all_comb) %>% 
  mutate(
         affected_upazila = ifelse(is.na(hh_size), NA, affected_upazila),
         treat_group = ifelse(is.na(hh_size), NA, treat_group))
# survey_year = ifelse(survey_round==1,2011,
#                               ifelse(survey_round==2,2015,
#                                      ifelse(survey_round==3,2018,NA))),

panelView::panelview( 1 ~ treat_group, gridOff = TRUE, by.timing = TRUE,
          data = all_comb, index = c("hh_id","survey_year"), display.all = TRUE,
          xlab = "Year", ylab = "Nbr household", pre.post = TRUE, by.unit=TRUE,  background = "white",cex.main = 20, cex.axis= 8, cex.lab = 12, cex.legend = 12, shade.post = TRUE, collapse.history = "TRUE", main = "Traitement status")
```

## Study Variables

### Socio-demographic variables

### Filtering to obtained only needed


#### Kid Sex/gender

```{r eval=FALSE, warning=FALSE, include=FALSE, results='hide'}

#
# r1_data %>%
#
#   # Selecting relevant variables
#   select(weight_kg,height_cm,if_not_measured_why,hhm_sex,hhm_age,relation_hhh, affected_upazila) %>%
#   #rename(affected_upazila=Affected_district) %>%
#    mutate(affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected district", "Affected district"), ordered = TRUE)) %>%
#   # Generate a summary table using "tbl_summary" for the specified columns
#   tbl_summary(
#     by = affected_upazila,
#      label = list(
#        weight_kg ~ "weight (kg)",
#        height_cm ~ "height (cm)",
#        hhm_sex ~ "Sex",
#        hhm_age ~ "age (in year)",
#        relation_hhh ~ "relation with the head",
#        if_not_measured_why ~ "Why missing"
#
#     ),
#     statistic = list(
#       all_categorical() ~ "{n} ({p}%)",
#       all_continuous() ~ "{mean} ({sd})"
#     ),
#     missing_text = "(Missing)",
#     digits = everything() ~ c(2,2),
#     missing = "always"
#   ) %>%
#     modify_caption("**R1**") %>%
#   # Modify the table header to provide a descriptive label
#   modify_header(label ~ "Affected Upazila") %>%
#   add_overall() %>%
#   add_n()%>%
#   # Add difference statistics to the table
#   add_difference()

#
#
# r1_data %>%
#
#   # Selecting relevant variables
#    select(weight_kg,height_cm,if_not_measured_why,hhm_sex,hhm_age,relation_hhh,affected_upazila) %>%
#   mutate(sample='round 1') %>%
#
#   plyr::rbind.fill(
#     #For the sibling dataset
#     r2_data %>%
# select(weight_kg,height_cm,if_not_measured_why,hhm_sex,hhm_age,relation_hhh, affected_upazila) %>%
#   #rename(affected_upazila=Affected_district) %>%
#    mutate(
#      sample='round 2',
#      affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected district", "Affected district"), ordered = TRUE)) %>%
#   filter(!is.na(if_not_measured_why))) %>%
#
#   tbl_strata(
#     strata = sample,
#     .tbl_fun =
#       ~ .x %>%
#       # Generate a summary table using "tbl_summary" for the specified columns
#       tbl_summary(
#     by = affected_upazila,
#      label = list(
#        weight_kg ~ "weight (kg)",
#        height_cm ~ "height (cm)",
#        hhm_sex ~ "Sex",
#        hhm_age ~ "age (in year)",
#        relation_hhh ~ "relation with the head",
#        if_not_measured_why ~ "Why missing"
#
#     ),
#     statistic = list(
#       all_categorical() ~ "{n} ({p}%)",
#       all_continuous() ~ "{mean} ({sd})"
#     ),
#     missing_text = "(Missing)",
#     digits = everything() ~ c(2,2),
#     missing = "always"
#   ) %>%
#       add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) %>%
#       # Modify the table header to provide a descriptive label
#       modify_header(label ~ "Characteristics of children"),
#     # Add difference statistics to the table
#     #add_difference(),
#     .header = "**{strata}**, N = {n}") #%>%
#   #as_gt() %>%
#   #gt::gtsave('desc_table_summary.tex', path = here::here())

```